### 2015-09-17 LatexTemplates/demo.tex
Initial commit

%Original version in April 2002 by Antje Endemann
%
%Adapted for usage in Student Conference course by jubo (050118).
%Optimized for usage with pdflatex. For usage with plain latex,
%figures must be in Postscript (.ps or .eps files) and additional
%packages must be imported.
%Last updated 100105 by jubo
%
%This template works for outline and annotated bibliography
%(deliverable 2) without any changes.
%For usage with full and final papers (deliverables 3 and 4a/b)
%you must make several changes. All necessary changes are
%described in three specific commented sections preceded by
%`%%%%% BEGIN OF ADJUSTMENTS SECTION %%%%%'.
%The changes are in order of appearance:
%   - adjust the `\documentclass' command
%   - uncomment the abstract section
%   - adjust the `\bibliographystyle' command

%%%%% BEGIN OF 1st ADJUSTMENTS SECTION %%%%%
% You must use only one of the following `\documentclass' commands
% For the outline and annotated bibliography (deliverable 2)
% you must use the following command:
%
\documentclass[runningheads,a4paper,oribibl]{llncs}
%
% For the full and final paper (deliverables 3 and 4a/b)
% you must use the command below (and put the one above in comments).
% In other words, the 'oribib' option must be used for Deliverable 2
% but not for 3 and 4a/b.
% 
%
%\documentclass[runningheads,a4paper]{llncs}
%
%%%%% END OF 1st ADJUSTMENTS SECTION %%%%%

\usepackage[T1]{fontenc}  %% needed for special characters (umlaut)
\usepackage[latin1]{inputenc}
\usepackage{graphicx}     %% for graphical things such as including pictures
\usepackage{url}          %% for proper formatting of URLs

\begin{document}

\pagestyle{headings}

\mainmatter

\title{Typesetting Your Outline, Annotated Bibliography, and Full Paper for the Course Student Conference in Computing Science\thanks{based on an earlier version by Jürgen Börstler}}

% The abbreviated title will be shown in the headers of even pages.
% You should use the full title unless it is too long.
\titlerunning{Example Outline and Annotated Bibliography}

\author{Frank Drewes}

\institute{
    Department of Computing Science \\
    Umeå University, Sweden \\
    \email{drewes@cs.umu.se}
}

\maketitle

%%%%% BEGIN OF 2nd ADJUSTMENTS SECTION %%%%%
% Do NOT include an abstract in the outline and annotated bibliography
% (deliverable 2). For the full and final paper (deliverables 3 and 4a/b),
% you must uncomment the following two commands and place your text for
% the abstract in between them.
%
% \begin{abstract}
%   Here goes the actual text of your abstract.
% \end{abstract}
%
%%%%% END OF 2nd ADJUSTMENTS SECTION %%%%%

\section{Introduction}
An outline is a draft of a research paper. It will help you to organize your thoughts, ideas and materials in a logical form. It should be detailed enough to make the following clear to yourself and
to the reader.
\begin{description}
   \item[Purpose] What exactly is (will be) the goal of your paper.
         You should therefore develop some kind of \emph{thesis statement},
         i.e., a specific statement, research question or hypothesis you
         want to answer or investigate in more detail.
   \item[Rationale/Motivation] Make clear why your thesis
         statement is interesting or important. A general motivation like
         ``I want to learn more about topic X'' definitely is not good enough.
   \item[Contents] What your final paper approximately will contain.
   \item[Resources] The resources you intend to use in your work. This
         will be specified in more detail in the annotated bibliography
         (reference section).
\end{description}

The main sections and subsections should be drafted and contain some
actual text or information about the planned contents, like the
following.
\begin{itemize}
  \item Meaningful section and subsection headers.
  \item Some (preliminary) text in all or most of the sections and subsections
        that help you organize your thoughts, ideas and materials. This will
        also give the reader (and yourself) a feeling for the planned contents.
  \item Citations of literature you intend to use to support your reasoning,
        like~\cite{beck:1989} or~\cite{booch:1999,fleury:2000,thimbleby:1999}.
  \item Drafts of figures (see Figure~\ref{fig:UML} and Figure~\ref{fig:picture}),
        tables (see Table~\ref{tab:table}), or examples.
\end{itemize}

\section{Annotated Bibliography}\label{sec:bibl}
The annotated bibliography is a list of literature references, where each
reference is followed by an ``annotation''. Please do not confuse this
annotation with an abstract. An annotation should describe and comment
the reference \emph{in your own words}, and it should focus on the aspects that
are \emph{important to you}.

The actual data of the annotated bibliography is stored in a separate text file, a
BIBTeX database such as the file \texttt{demo.bib}. Each entry describes a reference
and consists of a number of fields recording title, author, etc. Annotations
and other information can be stored in additional fields. Please note that you do
not need to delete any annotations from your BIBTeX file for later deliverables.
The annotations will be disregarded by BIBTeX because you will use a different
BIBTeX formatting style for the references in Deliverables~3 and~4a/b
(see the commented section at the end of \texttt{demo.bib}).

\section{Formatting Guidelines}
Please check the lecture overheads and the submission guidelines for
details on formatting and other requirements. The outline should consist of
about two pages plus the annotated bibliography.

\section{Subsections, Lists, Tables, and Figures}
Sections and subsections on the first and second levels
are numbered automatically. Subsections on levels three or more do not get
section numbers in the formatting style we use here.

\subsection{Lists}
Lists can be itemized, like in the list right before Section~\ref{sec:bibl},
or enumerated as below. Of course, lists can be nested.

\begin{enumerate}
  \item This is an example of a nested enumerated (numbered) list.
  \begin{enumerate}
     \item First subitem.
     \item Second subitem.
  \end{enumerate}
  \item Second item.
  \item And so on.
\end{enumerate}

\subsection{Tables}
Tables are constructed using the \texttt{tabular}
environment. For an example, please check the \LaTeX\ source code for
Table~\ref{tab:table}.
%
\begin{table}
   \centering
   \begin{tabular}{|l|p{2,8cm}|c|r|}
     \hline
     \textbf{left aligned} & \textbf{formatted as a paragraph} &
       \textbf{center aligned} & \textbf{right aligned}\\
     \hline
     row 2 &
       it is possible to have long texts in tables if they are
       formatted as a paragraph &
       this does not work well otherwise & 123\\
     row 3 & 45 & 6 & 7\\
     \hline
   \end{tabular}
   \caption{A simple table with 4 columns and 3 rows.\label{tab:table}}
\end{table}%
%
There are several useful extensions of the \texttt{tabular} environment. One of them
is \texttt{tabularx}, which lets you explicitly define the table width (normally
\texttt{\string\linewidth}) and has a column type \texttt X whose width is automatically calculated
from this. If you want to use it, load the package \texttt{tabularx} and have a look
at its documentation.

\subsection{Floating Tables and Figures}
Tables and figures should normally be put into the environments \texttt{table}
and \texttt{figure}, respectively. In this way, \LaTeX\ will automatically
attempt to move the table or figure to a place where it fits. Moreover, you can
(and should) give an informative caption and define a
symbolic label used to refer to them from the text. The labelling mechanism works
as follows. In or after the caption of the float, you place a the command
\texttt{\string\label\{my label\}}. Now \LaTeX\ will produce the numer of that
float in all places where you use the command \texttt{\string\ref\{my label\}}.
You can also refer to the page number on which the float appears by using the
command \texttt{\string\pageref\{my label\}}. For example, in the caption of
Table~\ref{tab:table} the command \texttt{\string\label\{tab:table\}} was used,
so that this sentence could refer to it by \texttt{Table\raisebox{-.5ex}{\string~}\string\ref\{tab:table\}}.
Note that a tilde is used instead of a space character between the word Table and the
referencing command. This creates a nonbreaking space, which prevents \LaTeX\ from
inserting a line break between the two. The probably obvious purpose is to avoid ugly linebreaks
such as Table \ref{tab:table}.\footnote{The same kind of nonbreaking space should be used in front of
\texttt{\string\pageref} and \texttt{\string\cite}, for the same reasons.}

The contents of a
``float'' can be any \LaTeX\ material, but tables often consist of \texttt{tabular}
material and figures often contain graphics imported via the command
\texttt{\string\includegraphics}.

In plain \LaTeX\ (\textit{latex}), imported graphics must be in \textit{PS/EPS} format.
If you use \textit{pdflatex}, which we strongly recommend,
you can include a range of different formats, like for example \textit{PDF}
(see Figure~\ref{fig:UML}) or \textit{JPG} (see Figure~\ref{fig:picture}).

\begin{figure}
   \centering
   \includegraphics[width=0.75\textwidth]{UMLdiagram}
   \caption{A figure from a PDF file (must be PDF 1.4 compatible).\label{fig:UML}}
\end{figure}

\begin{figure}
   \centering
   \includegraphics[width=\textwidth]{example_picture} % you can use other formats too
   \caption{Another figure; this time from a JPG file.\label{fig:picture}}
\end{figure}

As mentioned, \LaTeX\ automatically moves floats to a ``good'' place, normally near
the place where the environment is found in the source file. Thus, as a rule of thumb,
the environment should be placed near the position where you refer to the table or figure
for the first time, even though it could in principle be added anywhere. Many authors
have quite distinct ideas about the optimal placement of a float in the compiled paper.
In fact, this placement can be affected by optional arguments to the floating
environments. \emph{Please do not make use of these possibilities!} One reason is that
the automatic placement defined by the style (in this case the LNCS style) is intended
to create a uniform ``look and feel'' which is destroyed by manual formatting. The other,
more important reason is that including the paper in the proceedings may lead to
slight changes in, e.g., page breaks. In such cases, manually placed tables and figures
can end up in very unsatisfactory places.

\section{Further Remarks}

Below, some more hints are collected that you should use when preparing your full paper
and the final version. In fact, you should follows these recommendations from the very
beginning, because it saves time to do it right from the start.

\subsection{More about Manual Formatting}
In principle, \LaTeX\ gives you\\
\hspace*{-2em}all p\raisebox{1pt}os\hspace{.2ex}si\raisebox{-.5ex}bi\hspace{-.5ex}li\rotatebox{180}tie\scalebox{5}[1]s in the world\\[.5ex]
\hspace*{2em}for manual typesetting\\[-1.5ex]
\hspace*{2cm} in all kinds of weird ways.\footnote{In fact, this statement
is literally true to the extent possible, because \LaTeX\ 
is Turing complete. Thus, every computable layout can be implemented in \LaTeX.} Please refrain
from using them, including manual
linebreaks (except in places where these are intended to be used, e.g., to
end a row in a \texttt{tabular} environment), \texttt{\string\noindent}, \texttt{\string\bigskip},
and the like, the reasons basically being the same as those for avoiding manual placement
of floats. Of course, you should even more strictly refrain from changing general layout parameters such
as \texttt{\string\parskip} and \texttt{\string\parindent}.

\subsection{Referring to Internet Resources}

People use different ways to refer to homepages, forums, and other types of Internet resources.
Some treat them as ordinary references and include them in their reference section, such
as~\cite{bluej}. However, since such material is quite different in character from real scientific
publications, a cleaner solution is to use the reference section only for ordinary references and
add footnotes to point to other material, e.g., when writing about BlueJ\footnote{\url{http://www.buej.org},
BlueJ tool homepage, accessed 2005-01-12}. Note that, nowadays, even scientific publications
sometimes lack a printed version and are available only electronically (such as,
e.g.,~\cite{Corradini-Drewes:11}). Of course, such publications
should nevertheless be included in the list of references. The important point is not whether
material is printed or not, but which role it plays.

\section{A Checklist for the Full Version}

When your full version is complete and ready for submission, please spend a few minutes to
check the following, using the search facility of your favorite editor:
\begin{itemize}
\item You have taken care of the adjustments necessary to be made when switching from
the outline and annotated bibliography to the actual style of the article. In particular,
this means that you do not use the \texttt{oribibl} option in the \texttt{\string\documentclass}
command, the BIBTeX style used is \texttt{splncs}, and the command \texttt{\string\nocite\{*\}}
has been removed or commented out.
\item Words in the title of the paper and in section and subsection headings are correctly
capitalized.
\item Spaces in front of \texttt{\string\ref}, \texttt{\string\pageref}, and \texttt{\string\cite}
are nonbreaking. (Also, make sure that there actually \emph{are} spaces in front of them!) Again,
note that there might be small changes in the layout when the proceedings are produced. Therefore,
it is not guaranteed that all line breaks will stay the same.
\item Check the list of references carefully. If something is strange, correct
the corresponding record in your BIBTeX file. Note that names of authors and editors
in the \texttt{author} and \texttt{editor} fields should preferably be formatted according to
\texttt{last name(s), first name(s)}, and multiple authors/editors must be separated by the
keyword \texttt{and}. In titles, abbreviations such as UML should be enclosed in curly brackets
(i.e., \texttt{\{UML\}}) to prevent BIBTeX from turning them into lowercase.
\item Check whether you use ordinary double quotation marks \texttt" in your \LaTeX\ source. If
so, replace each by two single quotation marks: \verb;``; on the left and \verb;''; on the right,
thus turning, e.g., "fishy" into ``fishy''.
\item Typeset URLs by means of the command \texttt{\string\url}.
\end{itemize}

%%%%% BEGIN OF 3rd ADJUSTMENTS SECTION %%%%%
% For the outline and annotated bibliography (deliverable 2)
% you must use the following two commands:
%
\nocite{*}  % Includes ALL entries from the .bib-file, even if they are
            % not '\cite{}'-ed in the text above
\bibliographystyle{plain-annote}
%
%For the full and final paper (deliverables 3 and 4a/b)
% use ONLY the following commands (i.e. put the commands above into
% comments and uncomment the command below):
%
% \bibliographystyle{splncs}
%
%%%%% END OF ADJUSTMENTS SECTION %%%%%

\bibliography{demo}

\end{document}

### 2015-09-17 Outline.tex
Initial commit

--- 2015-09-17 LatexTemplates/demo.tex
@@
 
-\title{Typesetting Your Outline, Annotated Bibliography, and Full Paper for the Course Student Conference in Computing Science\thanks{based on an earlier version by Jürgen Börstler}}
+\title{Title goes here\thanks{based on an earlier version by Jürgen Börstler}}
 
@@
 %%%%% END OF 2nd ADJUSTMENTS SECTION %%%%%
-
-\section{Introduction}
-An outline is a draft of a research paper. It will help you to organize your thoughts, ideas and materials in a logical form. It should be detailed enough to make the following clear to yourself and
-to the reader.
-\begin{description}
-   \item[Purpose] What exactly is (will be) the goal of your paper.
-         You should therefore develop some kind of \emph{thesis statement},
-         i.e., a specific statement, research question or hypothesis you
-         want to answer or investigate in more detail.
-   \item[Rationale/Motivation] Make clear why your thesis
-         statement is interesting or important. A general motivation like
-         ``I want to learn more about topic X'' definitely is not good enough.
-   \item[Contents] What your final paper approximately will contain.
-   \item[Resources] The resources you intend to use in your work. This
-         will be specified in more detail in the annotated bibliography
-         (reference section).
-\end{description}
-
-The main sections and subsections should be drafted and contain some
-actual text or information about the planned contents, like the
-following.
-\begin{itemize}
-  \item Meaningful section and subsection headers.
-  \item Some (preliminary) text in all or most of the sections and subsections
-        that help you organize your thoughts, ideas and materials. This will
-        also give the reader (and yourself) a feeling for the planned contents.
-  \item Citations of literature you intend to use to support your reasoning,
-        like~\cite{beck:1989} or~\cite{booch:1999,fleury:2000,thimbleby:1999}.
-  \item Drafts of figures (see Figure~\ref{fig:UML} and Figure~\ref{fig:picture}),
-        tables (see Table~\ref{tab:table}), or examples.
-\end{itemize}
-
-\section{Annotated Bibliography}\label{sec:bibl}
-The annotated bibliography is a list of literature references, where each
-reference is followed by an ``annotation''. Please do not confuse this
-annotation with an abstract. An annotation should describe and comment
-the reference \emph{in your own words}, and it should focus on the aspects that
-are \emph{important to you}.
-
-The actual data of the annotated bibliography is stored in a separate text file, a
-BIBTeX database such as the file \texttt{demo.bib}. Each entry describes a reference
-and consists of a number of fields recording title, author, etc. Annotations
-and other information can be stored in additional fields. Please note that you do
-not need to delete any annotations from your BIBTeX file for later deliverables.
-The annotations will be disregarded by BIBTeX because you will use a different
-BIBTeX formatting style for the references in Deliverables~3 and~4a/b
-(see the commented section at the end of \texttt{demo.bib}).
-
-\section{Formatting Guidelines}
-Please check the lecture overheads and the submission guidelines for
-details on formatting and other requirements. The outline should consist of
-about two pages plus the annotated bibliography.
-
-\section{Subsections, Lists, Tables, and Figures}
-Sections and subsections on the first and second levels
-are numbered automatically. Subsections on levels three or more do not get
-section numbers in the formatting style we use here.
-
-\subsection{Lists}
-Lists can be itemized, like in the list right before Section~\ref{sec:bibl},
-or enumerated as below. Of course, lists can be nested.
-
-\begin{enumerate}
-  \item This is an example of a nested enumerated (numbered) list.
-  \begin{enumerate}
-     \item First subitem.
-     \item Second subitem.
-  \end{enumerate}
-  \item Second item.
-  \item And so on.
-\end{enumerate}
-
-\subsection{Tables}
-Tables are constructed using the \texttt{tabular}
-environment. For an example, please check the \LaTeX\ source code for
-Table~\ref{tab:table}.
-%
-\begin{table}
-   \centering
-   \begin{tabular}{|l|p{2,8cm}|c|r|}
-     \hline
-     \textbf{left aligned} & \textbf{formatted as a paragraph} &
-       \textbf{center aligned} & \textbf{right aligned}\\
-     \hline
-     row 2 &
-       it is possible to have long texts in tables if they are
-       formatted as a paragraph &
-       this does not work well otherwise & 123\\
-     row 3 & 45 & 6 & 7\\
-     \hline
-   \end{tabular}
-   \caption{A simple table with 4 columns and 3 rows.\label{tab:table}}
-\end{table}%
-%
-There are several useful extensions of the \texttt{tabular} environment. One of them
-is \texttt{tabularx}, which lets you explicitly define the table width (normally
-\texttt{\string\linewidth}) and has a column type \texttt X whose width is automatically calculated
-from this. If you want to use it, load the package \texttt{tabularx} and have a look
-at its documentation.
-
-\subsection{Floating Tables and Figures}
-Tables and figures should normally be put into the environments \texttt{table}
-and \texttt{figure}, respectively. In this way, \LaTeX\ will automatically
-attempt to move the table or figure to a place where it fits. Moreover, you can
-(and should) give an informative caption and define a
-symbolic label used to refer to them from the text. The labelling mechanism works
-as follows. In or after the caption of the float, you place a the command
-\texttt{\string\label\{my label\}}. Now \LaTeX\ will produce the numer of that
-float in all places where you use the command \texttt{\string\ref\{my label\}}.
-You can also refer to the page number on which the float appears by using the
-command \texttt{\string\pageref\{my label\}}. For example, in the caption of
-Table~\ref{tab:table} the command \texttt{\string\label\{tab:table\}} was used,
-so that this sentence could refer to it by \texttt{Table\raisebox{-.5ex}{\string~}\string\ref\{tab:table\}}.
-Note that a tilde is used instead of a space character between the word Table and the
-referencing command. This creates a nonbreaking space, which prevents \LaTeX\ from
-inserting a line break between the two. The probably obvious purpose is to avoid ugly linebreaks
-such as Table \ref{tab:table}.\footnote{The same kind of nonbreaking space should be used in front of
-\texttt{\string\pageref} and \texttt{\string\cite}, for the same reasons.}
-
-The contents of a
-``float'' can be any \LaTeX\ material, but tables often consist of \texttt{tabular}
-material and figures often contain graphics imported via the command
-\texttt{\string\includegraphics}.
-
-In plain \LaTeX\ (\textit{latex}), imported graphics must be in \textit{PS/EPS} format.
-If you use \textit{pdflatex}, which we strongly recommend,
-you can include a range of different formats, like for example \textit{PDF}
-(see Figure~\ref{fig:UML}) or \textit{JPG} (see Figure~\ref{fig:picture}).
-
-\begin{figure}
-   \centering
-   \includegraphics[width=0.75\textwidth]{UMLdiagram}
-   \caption{A figure from a PDF file (must be PDF 1.4 compatible).\label{fig:UML}}
-\end{figure}
-
-\begin{figure}
-   \centering
-   \includegraphics[width=\textwidth]{example_picture} % you can use other formats too
-   \caption{Another figure; this time from a JPG file.\label{fig:picture}}
-\end{figure}
-
-As mentioned, \LaTeX\ automatically moves floats to a ``good'' place, normally near
-the place where the environment is found in the source file. Thus, as a rule of thumb,
-the environment should be placed near the position where you refer to the table or figure
-for the first time, even though it could in principle be added anywhere. Many authors
-have quite distinct ideas about the optimal placement of a float in the compiled paper.
-In fact, this placement can be affected by optional arguments to the floating
-environments. \emph{Please do not make use of these possibilities!} One reason is that
-the automatic placement defined by the style (in this case the LNCS style) is intended
-to create a uniform ``look and feel'' which is destroyed by manual formatting. The other,
-more important reason is that including the paper in the proceedings may lead to
-slight changes in, e.g., page breaks. In such cases, manually placed tables and figures
-can end up in very unsatisfactory places.
-
-\section{Further Remarks}
-
-Below, some more hints are collected that you should use when preparing your full paper
-and the final version. In fact, you should follows these recommendations from the very
-beginning, because it saves time to do it right from the start.
-
-\subsection{More about Manual Formatting}
-In principle, \LaTeX\ gives you\\
-\hspace*{-2em}all p\raisebox{1pt}os\hspace{.2ex}si\raisebox{-.5ex}bi\hspace{-.5ex}li\rotatebox{180}tie\scalebox{5}[1]s in the world\\[.5ex]
-\hspace*{2em}for manual typesetting\\[-1.5ex]
-\hspace*{2cm} in all kinds of weird ways.\footnote{In fact, this statement
-is literally true to the extent possible, because \LaTeX\ 
-is Turing complete. Thus, every computable layout can be implemented in \LaTeX.} Please refrain
-from using them, including manual
-linebreaks (except in places where these are intended to be used, e.g., to
-end a row in a \texttt{tabular} environment), \texttt{\string\noindent}, \texttt{\string\bigskip},
-and the like, the reasons basically being the same as those for avoiding manual placement
-of floats. Of course, you should even more strictly refrain from changing general layout parameters such
-as \texttt{\string\parskip} and \texttt{\string\parindent}.
-
-\subsection{Referring to Internet Resources}
-
-People use different ways to refer to homepages, forums, and other types of Internet resources.
-Some treat them as ordinary references and include them in their reference section, such
-as~\cite{bluej}. However, since such material is quite different in character from real scientific
-publications, a cleaner solution is to use the reference section only for ordinary references and
-add footnotes to point to other material, e.g., when writing about BlueJ\footnote{\url{http://www.buej.org},
-BlueJ tool homepage, accessed 2005-01-12}. Note that, nowadays, even scientific publications
-sometimes lack a printed version and are available only electronically (such as,
-e.g.,~\cite{Corradini-Drewes:11}). Of course, such publications
-should nevertheless be included in the list of references. The important point is not whether
-material is printed or not, but which role it plays.
-
-\section{A Checklist for the Full Version}
-
-When your full version is complete and ready for submission, please spend a few minutes to
-check the following, using the search facility of your favorite editor:
-\begin{itemize}
-\item You have taken care of the adjustments necessary to be made when switching from
-the outline and annotated bibliography to the actual style of the article. In particular,
-this means that you do not use the \texttt{oribibl} option in the \texttt{\string\documentclass}
-command, the BIBTeX style used is \texttt{splncs}, and the command \texttt{\string\nocite\{*\}}
-has been removed or commented out.
-\item Words in the title of the paper and in section and subsection headings are correctly
-capitalized.
-\item Spaces in front of \texttt{\string\ref}, \texttt{\string\pageref}, and \texttt{\string\cite}
-are nonbreaking. (Also, make sure that there actually \emph{are} spaces in front of them!) Again,
-note that there might be small changes in the layout when the proceedings are produced. Therefore,
-it is not guaranteed that all line breaks will stay the same.
-\item Check the list of references carefully. If something is strange, correct
-the corresponding record in your BIBTeX file. Note that names of authors and editors
-in the \texttt{author} and \texttt{editor} fields should preferably be formatted according to
-\texttt{last name(s), first name(s)}, and multiple authors/editors must be separated by the
-keyword \texttt{and}. In titles, abbreviations such as UML should be enclosed in curly brackets
-(i.e., \texttt{\{UML\}}) to prevent BIBTeX from turning them into lowercase.
-\item Check whether you use ordinary double quotation marks \texttt" in your \LaTeX\ source. If
-so, replace each by two single quotation marks: \verb;``; on the left and \verb;''; on the right,
-thus turning, e.g., "fishy" into ``fishy''.
-\item Typeset URLs by means of the command \texttt{\string\url}.
-\end{itemize}
-
-%%%%% BEGIN OF 3rd ADJUSTMENTS SECTION %%%%%
-% For the outline and annotated bibliography (deliverable 2)
-% you must use the following two commands:
-%
-\nocite{*}  % Includes ALL entries from the .bib-file, even if they are
-            % not '\cite{}'-ed in the text above
-\bibliographystyle{plain-annote}
-%
-%For the full and final paper (deliverables 3 and 4a/b)
-% use ONLY the following commands (i.e. put the commands above into
-% comments and uncomment the command below):
-%
-% \bibliographystyle{splncs}
-%
-%%%%% END OF ADJUSTMENTS SECTION %%%%%
-
-\bibliography{demo}
-
-\end{document}

### 2015-09-18 Outline.tex
Continued working on the outline

@@
 
-\title{Title goes here\thanks{based on an earlier version by Jürgen Börstler}}
+\title{Guidelines for Designing Touch Interfaces for Controlling Robotic Nozzles in Critical Emergency Situations. \thanks{wtf}}
 
@@
 % You should use the full title unless it is too long.
-\titlerunning{Example Outline and Annotated Bibliography}
+\titlerunning{Touch Interfaces for Robotic Nozzles}
 
-\author{Frank Drewes}
+\author{Albin Hübsch}
 
@@
 	Umeå University, Sweden \\
-	\email{drewes@cs.umu.se}
+	\email{id11ahh@cs.umu.se}
 }
@@
 %%%%% END OF 2nd ADJUSTMENTS SECTION %%%%%
+
+\section{Introduction}
+Here goes text. Write about Purpose, Motivation, Contents and Resources.
+
+\begin{description}
+	\item[Purpose of the paper] Well, explain the purpose of the paper.
+	\item[Motivation for the paper] Make clear why this paper needs to be done.
+	\item[Content] The final paper will include...
+	\item[Resources] Resources I we plan to use in the work of this paper.
+\end{description}
+
+\section{Method}
+The main goal with this paper is to evaluate if increased color contrast in a touch screen interface for controlling robotic nozzles can result in zero faulty interactions with the touch interface in emergency situations.
+
+\subsection{Design of an A/B test}
+In order to test if increased color contrast in a touch interface can completedly remove all faulty interactions an A/B test was conducted.
+\emph{This section will contain a short but descriptive text about how the A/B test was prepared, built and performed. It will describe who participated}.
+
+\subsection{Evaluation of the A/B test}
+This section will in short describe the evaluation process of the A/B test. How the test results were collected and what parameters we've had focus on during the test.
+
+\section{Result}
+All results produced from these tests are here presented with clear numbers
+
+\subsection{A/B test}
+text about a/b test results
+
+\subsection{Evaluation}
+text about the results that came out of the evaluation.
+
+\section{Discussion}
+In this section we'll discuss the results from the tests. We'll discuss what the results mean and how they should, and could be interpreted.
+
+\subsection{Conclusions and Guidelines}
+Here we'll present our conclusions based on the resulting outcome from the tests.
+We'll also present our four guidelines on how to design a touch interface compatible for emergency situations.
+These guidlines will be created based on the test results.
+
+\subsection{Drawbacks and Limitations}
+Present drawbacks and limitations with both the used method and the produced results.
+Time is limited, therefore a bullet proof test can not be performed which means the results will somewhat be limited in credibility.
+
+\subsection{Future Work}
+Due to the limited time we have on this paper there will be alot of things that can be improved. We'll in this section give our suggestions on things that could be done in future or continued work.
+
+%%%%% BEGIN OF 3rd ADJUSTMENTS SECTION %%%%%
+% For the outline and annotated bibliography (deliverable 2)
+% you must use the following two commands:
+%
+\nocite{*}  % Includes ALL entries from the .bib-file, even if they are
+            % not '\cite{}'-ed in the text above
+\bibliographystyle{plain-annote}
+%
+% For the full and final paper (deliverables 3 and 4a/b)
+% use ONLY the following commands (i.e. put the commands above into
+% comments and uncomment the command below):
+%
+% \bibliographystyle{splncs}
+%
+%%%%% END OF ADJUSTMENTS SECTION %%%%%
+
+\bibliography{demo}
+
+\end{document}

### 2015-09-22 Outline.tex
Continued working on Outline, milestone before annotations

@@
 \section{Introduction}
-Here goes text. Write about Purpose, Motivation, Contents and Resources.
+Introduction part will contain a purpose of the paper and a motivation for why the paper was made.
 
 \begin{description}
-	\item[Purpose of the paper] Well, explain the purpose of the paper.
-	\item[Motivation for the paper] Make clear why this paper needs to be done.
-	\item[Content] The final paper will include...
-	\item[Resources] Resources I we plan to use in the work of this paper.
+	\item[Purpose of the paper] Can a well designed touch interface for controlling robotic nozzles reach a level of zero faulty interactions in critical emergency situations by increasing the color contrast of the interface?
+	\item[Motivation for the paper] In critical emergency situations, like in the case of fire, a graphical touch user interface should not be the weak link on getting the job done when controlling robotic nozzles.
+One single press on the wrong button can be the difference between life or death.
 \end{description}
@@
 \subsection{Design of an A/B test}
-In order to test if increased color contrast in a touch interface can completedly remove all faulty interactions an A/B test was conducted.
+In order to test if increased color contrast in a touch interface can completely remove all faulty interactions an A/B test was conducted.
 \emph{This section will contain a short but descriptive text about how the A/B test was prepared, built and performed. It will describe who participated}.
@@
 \section{Result}
-All results produced from these tests are here presented with clear numbers
-
-\subsection{A/B test}
-text about a/b test results
+All results produced from the tests are here presented with clear numbers and conclusions.
 
 \subsection{Evaluation}
-text about the results that came out of the evaluation.
+The evaluation itself and a text about the evaluation results.
 
@@
 We'll also present our four guidelines on how to design a touch interface compatible for emergency situations.
-These guidlines will be created based on the test results.
+These guidelines will be created based on the test results.
 
@@
 \subsection{Future Work}
-Due to the limited time we have on this paper there will be alot of things that can be improved. We'll in this section give our suggestions on things that could be done in future or continued work.
+Due to the limited time we have on this paper there will be a lot of things that can be improved. We'll in this section give our suggestions on things that could be done in future or continued work.
 

### 2015-09-25 Outline.tex
Added bib file
Updates to annotations
Hand in of Outline for Peer Review

@@
 \usepackage[T1]{fontenc}  %% needed for special characters (umlaut)
-\usepackage[latin1]{inputenc}
+\usepackage[utf8]{inputenc}
 \usepackage{graphicx}     %% for graphical things such as including pictures
@@
 
-\title{Guidelines for Designing Touch Interfaces for Controlling Robotic Nozzles in Critical Emergency Situations. \thanks{wtf}}
+\title{Guidelines for Designing Touch Interfaces for Controlling Robotic Nozzles in Critical Emergency Situations.}
 
@@
 % You should use the full title unless it is too long.
-\titlerunning{Touch Interfaces for Robotic Nozzles}
+\titlerunning{Touch Interfaces for Robotic Nozzles in Emergency Situations}
 
@@
 \subsection{Design of an A/B test}
-In order to test if increased color contrast in a touch interface can completely remove all faulty interactions an A/B test was conducted.
+In order to test if increased color contrast in a touch interface can  completely remove all faulty interactions an A/B test will be performed.
+Two identical applications, despite differences in color contrast, with just a few buttons will be measured against each other.
+We will measure time and errors.
+The test will have a time pressure to simulate an emergency situation.
+Instructions will be given on a secondary screen.
 \emph{This section will contain a short but descriptive text about how the A/B test was prepared, built and performed. It will describe who participated}.
@@
 
-\bibliography{demo}
+\bibliography{Bibliography}
 

### 2015-10-08 Outline.tex
Fixes to the outline

@@
 \begin{description}
-	\item[Purpose of the paper] Can a well designed touch interface for controlling robotic nozzles reach a level of zero faulty interactions in critical emergency situations by increasing the color contrast of the interface?
-	\item[Motivation for the paper] In critical emergency situations, like in the case of fire, a graphical touch user interface should not be the weak link on getting the job done when controlling robotic nozzles.
-One single press on the wrong button can be the difference between life or death.
+	\item[Purpose] Can a well designed touch interface with differences in color contrast for controlling robotic water cannon nozzles reach a lower level of faulty interactions in emergency situations.
+	\item[Motivation] In critical emergency situations, like in the case of fire, a graphical touch user interface should not be the weak link on getting the job done when controlling robotic water cannon nozzles.
+One wrong push of a touch screen button in the interface can be the difference between life or death.
 \end{description}
+The main goal with this paper is to evaluate if increased color contrast in a touch screen interface for controlling robotic water cannon nozzles can result in fewer faulty interactions, compared to a low contrast touch interface, in emergency situations.
+And from this we will present four guidelines on how to design a good touch interface for emergency situations.
+These guidelines will be useful for anyone designing touch interfaces made for demanding situations.
 
 \section{Method}
-The main goal with this paper is to evaluate if increased color contrast in a touch screen interface for controlling robotic nozzles can result in zero faulty interactions with the touch interface in emergency situations.
+In order to be able to test if increased color contrast has an substantial impact on the usability of a touch interface we will design two identical touch interfaces for controlling robotic water cannon nozzles.
+The only difference between these interfaces will be the color contrast.
+When designing the touch interface we will follow guidelines defined in the found references.
+Later these two interfaces will be tested by an A/B test.
+The test will then be evaluated to produce a result and a conclusion and finally form our four design guidelines.
 
 \subsection{Design of an A/B test}
-In order to test if increased color contrast in a touch interface can  completely remove all faulty interactions an A/B test will be performed.
-Two identical applications, despite differences in color contrast, with just a few buttons will be measured against each other.
-We will measure time and errors.
-The test will have a time pressure to simulate an emergency situation.
-Instructions will be given on a secondary screen.
+In order to test if increased color contrast can lower faulty interactions in a touch interface an A/B test will be developed and performed.
+Two identical applications, despite differences in color contrast, with just a few touch screen buttons will be measured against each other.
+We will measure both time and amount of errors it takes to perform each given task.
+The test persons will be told that there is a time limit and they have to do it as fast as they can in order to simulate an emergency situation.
+Instructions will be given on a secondary screen so that every test is consistent.
+
 \emph{This section will contain a short but descriptive text about how the A/B test was prepared, built and performed. It will describe who participated}.
@@
 \subsection{Evaluation of the A/B test}
-This section will in short describe the evaluation process of the A/B test. How the test results were collected and what parameters we've had focus on during the test.
+This section will in short describe the evaluation process of the A/B test. How the test results were collected and what parameters we have had focus on during the test.
 
 \section{Result}
-All results produced from the tests are here presented with clear numbers and conclusions.
+All results produced from the tests are here presented with clear numbers, conclusions and figures/graphics.
 
@@
 \section{Discussion}
-In this section we'll discuss the results from the tests. We'll discuss what the results mean and how they should, and could be interpreted.
+In this section we will discuss the results from the tests. We will discuss what the results mean and how they should and could be interpreted.
 
 \subsection{Conclusions and Guidelines}
-Here we'll present our conclusions based on the resulting outcome from the tests.
-We'll also present our four guidelines on how to design a touch interface compatible for emergency situations.
+Here we will present our conclusions based on the resulting outcome from the tests.
+We will also present our four guidelines on how to design a touch interface compatible for emergency situations.
 These guidelines will be created based on the test results.
@@
 \subsection{Future Work}
-Due to the limited time we have on this paper there will be a lot of things that can be improved. We'll in this section give our suggestions on things that could be done in future or continued work.
+Due to the limited time we have on this paper there will be a lot of things that can be improved. We will in this section give our suggestions on things that could be done in future or continued work.
 

### 2015-10-25 Paper.tex
cont. working

%Original version in April 2002 by Antje Endemann
%
%Adapted for usage in Student Conference course by jubo (050118).
%Optimized for usage with pdflatex. For usage with plain latex,
%figures must be in Postscript (.ps or .eps files) and additional
%packages must be imported.
%Last updated 100105 by jubo
%
%This template works for outline and annotated bibliography
%(deliverable 2) without any changes.
%For usage with full and final papers (deliverables 3 and 4a/b)
%you must make several changes. All necessary changes are
%described in three specific commented sections preceded by
%`%%%%% BEGIN OF ADJUSTMENTS SECTION %%%%%'.
%The changes are in order of appearance:
%   - adjust the `\documentclass' command
%   - uncomment the abstract section
%   - adjust the `\bibliographystyle' command

%%%%% BEGIN OF 1st ADJUSTMENTS SECTION %%%%%
% You must use only one of the following `\documentclass' commands
% For the outline and annotated bibliography (deliverable 2)
% you must use the following command:
%
\documentclass[runningheads,a4paper,oribibl]{llncs}
%
% For the full and final paper (deliverables 3 and 4a/b)
% you must use the command below (and put the one above in comments).
% In other words, the 'oribib' option must be used for Deliverable 2
% but not for 3 and 4a/b.
% 
%
\documentclass[runningheads,a4paper]{llncs}
%
%%%%% END OF 1st ADJUSTMENTS SECTION %%%%%

\usepackage[T1]{fontenc}  %% needed for special characters (umlaut)
\usepackage[utf8]{inputenc}
\usepackage{graphicx}     %% for graphical things such as including pictures
\usepackage{url}          %% for proper formatting of URLs

\begin{document}

\pagestyle{headings}

\mainmatter

% \title{Guidelines for Designing Touch Interfaces for Controlling Robotic Nozzles in Critical Emergency Situations.}

\title{Can a high color contrast touch interface increase user reaction time when using a smart phone web based application.}

% response
% reaction time

% The abbreviated title will be shown in the headers of even pages.
% You should use the full title unless it is too long.

% \titlerunning{Touch Interfaces for Robotic Nozzles in Emergency Situations}

\titlerunning{asd}

\author{Albin Hübsch}

\institute{
	Department of Computing Science \\
	Umeå University, Sweden \\
	\email{id11ahh@cs.umu.se}
}

\maketitle

%%%%% BEGIN OF 2nd ADJUSTMENTS SECTION %%%%%
% Do NOT include an abstract in the outline and annotated bibliography
% (deliverable 2). For the full and final paper (deliverables 3 and 4a/b),
% you must uncomment the following two commands and place your text for
% the abstract in between them.
%
\begin{abstract}
Here goes paper abstract
\end{abstract}
%
%%%%% END OF 2nd ADJUSTMENTS SECTION %%%%%

\section{Introduction}
The main goal with this paper is to evaluate if color contrast has a significant impact on reaction time and usability in web based smart-phone applications. Consumer touch screen devices such as smart-phones has rapidly increased in amount and availability recent years. The touch screen technology have made great advances ~\cite{jennings2013touch} and it is more frequently used as a way of receiving user input. When technology moves to a broader audience, higher demands on usability needs to be set~\cite{gong2004guidelines}.

=== OLD BELOW

The main goal with this paper is to evaluate if color contrast has a significant impact on usability when using a touch screen smart phone application for controlling robotic nozzles in emergency situations. From the results we will suggest four design guidelines to be used when designing applications for similar use or in similar situations. Consumer touch screen devices such as smart phones has increased in amount rapidly recent years and the touch screen technology have made great advances~\cite{jennings2013touch}. Since these devices now are available to almost everyone, higher demands on usability needs to be set~\cite{paredes2014sosphone}.

Unifire, a company that builds robotic nozzles for water cannons has just introduced a controlling system to steer the nozzles from an application that can run on almost all touch screen smart phones (2015). But the use cases of this application, often in different emergency situations sets high demands on great usability. Defining great usability as fast and low on user input errors. A simplified version of this nozzle control application was modified to be used in these test.

\section{Method}
In order to be able to test if color contrast has an substantial impact on the usability of a touch user interface we have two versions of the same simplified application for controlling robotic nozzles. The only difference between the two versions is that the first one has the characteristics of low contrast and the second one high contrast. We conducted an A/B test to measure the usability performance of the two versions. The usability performance was measured using two parameters, time and errors.
\begin{description}
\item[Time] is measured to be able to see if one version is faster.
\item[Errors] are calculated to see if one of the versions tend to produce more user error inputs.
\end{description}

\subsection{Designing the A/B test}
The conducted A/B test consists of two versions of the same application. One high contrast and one low contrast. Both applications are simplified versions of the robotic nozzle controlling application. We simplified the application by exchanging all icons to more basic shapes like square, circle, triangle and a rhomb. ~\ref{fig:application}) or \textit{PNG}

The application consists of 4 soft buttons, each representing a function. We designed a program to give instructions on a secondary monitor. The instructions was a series of shapes equally to the shapes in the application and the test persons where told to press the representative shape in the application as fast as they could to simulate an stressful situation. If they pressed the wrong button they where told just to continue and press the right one. Both the application and the instruction program are logging timestamps for all input and counting user input errors.

Each version of the application was tested on [NUMBER PLACEHOLDER] persons all within the same age group (20-30) and with a variety of backgrounds.

\subsection{Evaluation of the A/B test}
This section will in short describe the evaluation process of the A/B test. How the test results were collected and what parameters we have had focus on during the test.

\section{Result}
All results produced from the tests are here presented with clear numbers, conclusions and figures/graphics.

\subsection{Evaluation}
The evaluation itself and a text about the evaluation results.

\section{Discussion}
In this section we will discuss the results from the tests. We will discuss what the results mean and how they should and could be interpreted.

\subsection{Conclusions and Guidelines}
Here we will present our conclusions based on the resulting outcome from the tests. We will also present our four guidelines on how to design a touch interface compatible for emergency situations. These guidelines will be created based on the test results.

Below follows our guidelines that we have designed from our test results. The guidelines can be used when designing a

\subsection{Drawbacks and Limitations}
This paper should not be used as a scientific foundation for any kind of argument. There are to many parameters affecting the results. Time limitation during the research period had a big influence on the credibility of the whole paper. We would like to emphasize some of the biggest drawbacks in the research and the paper by listing them below. \emph{Note that it is highly possible that there exists drawbacks not mentioned here}.

\begin{description}
	\item[Our group of test subjects was to small] To be able to get a more statistical valid result the test group has to be bigger.
	\item[Possibly bad simulation of emergency situation] Due to the limited time reserved for this paper and its research a true simulation of an emergency situation could not be set. We did our best but it could had been done better.
	\item[Many affecting parameters] The prototype is simple in its appearance but there are still many parameters that can affect the user interaction. Icons, icon size, optimal number of soft-buttons etc. All this, and more, should have been researched if done again. 
\end{description}

\subsection{Future Work}
Due to extremely limited time given for this paper there are many things that could be improved, made differently or simply just continued to be worked on. We have some concrete suggestions that could be a case for future work.

\begin{itemize}
	\item Extend the test group with more subjects. The patterns that slightly appeared in our results could with a bigger test group be more significant.
	\item Make the same tests but with a better simulation of an emergency situation. Our proposal to this is to stage an emergent situation and make the test person interact with the complete situation.
	\item Our collected test data can be downloaded and used freely to investigate other aspect not mentioned in this paper. One proposal is to look at the different shapes and try to detect possible error patterns between them.
\end{itemize}

%%%%% BEGIN OF 3rd ADJUSTMENTS SECTION %%%%%
% For the outline and annotated bibliography (deliverable 2)
% you must use the following two commands:
%
\nocite{*}  % Includes ALL entries from the .bib-file, even if they are
            % not '\cite{}'-ed in the text above
% \bibliographystyle{plain-annote}
%
% For the full and final paper (deliverables 3 and 4a/b)
% use ONLY the following commands (i.e. put the commands above into
% comments and uncomment the command below):
%
\bibliographystyle{splncs}
%
%%%%% END OF ADJUSTMENTS SECTION %%%%%

\bibliography{Bibliography}

\end{document}

### 2015-11-04 Paper.tex
keep working

@@
 %
-\documentclass[runningheads,a4paper,oribibl]{llncs}
+% \documentclass[runningheads,a4paper,oribibl]{llncs}
 %
@@
 
-\titlerunning{asd}
+\titlerunning{Can high color contrast increase user reaction time}
 
@@
 \section{Introduction}
-The main goal with this paper is to evaluate if color contrast has a significant impact on reaction time and usability in web based smart-phone applications.
+The main goal with this paper is to evaluate if color contrast has a significant impact on usability in web based smart-phone applications.
 Consumer touch screen devices such as smart-phones has rapidly increased in amount and availability recent years.
 The touch screen technology have made great advances ~\cite{jennings2013touch} and it is more frequently used as a way of receiving user input.
-When technology moves to a broader audience, higher demands on usability needs to be set~\cite{gong2004guidelines}.
+When this technology moves to a broader audience, higher demands on usability needs to be set~\cite{gong2004guidelines}.
+To further explore how usability can be improved using touch screen technology we are in this paper investigating if reaction time (referred to as RT in this paper) and user input errors (referred to as IE in this paper) can reach better results by increasing color contrast within the interface.
+Earlier work done in this field are exploring how we perceive different color contrast and how it can affect our reading performance~\cite{wu2003improving}.
+It has also been proved that Chromaticity, Contrast, and Cone Opponency in color space can affect RTs~\cite{mckeefry2003simple}.
+Many best practices for Mobile development also shows that "requirements for sufficient color contrast"~\cite{marcus2013design} must be meet to best exaggerate the content.
+But still the question remains, if a high color contrast interface can increase the the RT\footnote{Reaction time: the time it takes for a user to react on instructions} and decrease user IE\footnote{Input errors: the number of user input errors when interacting with a system}.
 
-=== OLD BELOW
-
-The main goal with this paper is to evaluate if color contrast has a significant impact on usability when using a touch screen smart phone application for controlling robotic nozzles in emergency situations.
-From the results we will suggest four design guidelines to be used when designing applications for similar use or in similar situations.
-Consumer touch screen devices such as smart phones has increased in amount rapidly recent years and the touch screen technology have made great advances~\cite{jennings2013touch}.
-Since these devices now are available to almost everyone, higher demands on usability needs to be set~\cite{paredes2014sosphone}.
-
-Unifire, a company that builds robotic nozzles for water cannons has just introduced a controlling system to steer the nozzles from an application that can run on almost all touch screen smart phones (2015).
-But the use cases of this application, often in different emergency situations sets high demands on great usability.
-Defining great usability as fast and low on user input errors.
-A simplified version of this nozzle control application was modified to be used in these test.
+High RTs and low user IE are especially desirable when designing user interfaces for situations with high demands on quick user input and low error tolerance such as emergency situations.
+The results of this paper can be used by any designer or developer.
 
 \section{Method}
-In order to be able to test if color contrast has an substantial impact on the usability of a touch user interface we have two versions of the same simplified application for controlling robotic nozzles.
-The only difference between the two versions is that the first one has the characteristics of low contrast and the second one high contrast.
-We conducted an A/B test to measure the usability performance of the two versions.
-The usability performance was measured using two parameters, time and errors.
-\begin{description}
-\item[Time] is measured to be able to see if one version is faster.
-\item[Errors] are calculated to see if one of the versions tend to produce more user error inputs.
-\end{description}
+In order to be able to test if color contrast has an substantial impact on the RT and user IE of a touch user interface we have designed a simple web application for an Android smart-phone.
+The application exists in two versions, one with low color (LC) contrast and one with high color contrast (HC) as can be seen in Fig~\ref{fig:application}.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{application}
+	\caption{Our two color contrast versions of our application designed.\label{fig:application}}
+\end{figure}
+
+We designed the application by following design guidelines given here~\cite{hoober2011designing} and~\cite{johnson2013designing}.
 
 \subsection{Designing the A/B test}
-The conducted A/B test consists of two versions of the same application.
-One high contrast and one low contrast.
-Both applications are simplified versions of the robotic nozzle controlling application.
-We simplified the application by exchanging all icons to more basic shapes like square, circle, triangle and a rhomb.
-~\ref{fig:application}) or \textit{PNG}
+We conducted an A/B test to measure the differences in RT and IE between the two versions.
+An A/B test is a commonly used method by developers and designers to test differences in performance between applications when the differentiated factors are known~\cite{johnson2013designing}.
+As in this case our known factor is the contrast difference.
 
-The application consists of 4 soft buttons, each representing a function.
-We designed a program to give instructions on a secondary monitor.
-The instructions was a series of shapes equally to the shapes in the application and the test persons where told to press the representative shape in the application as fast as they could to simulate an stressful situation.
-If they pressed the wrong button they where told just to continue and press the right one.
-Both the application and the instruction program are logging timestamps for all input and counting user input errors.
+The application consists of 4 buttons~\footnote{On screen button}, each button representing a function.
+To fraction each button from the others we put a unique shape in each button.
+The shapes we used are a, square, circle, triangle and a rhomb~\ref{fig:application}.
 
-Each version of the application was tested on [NUMBER PLACEHOLDER] persons all within the same age group (20-30) and with a variety of backgrounds.
+To be able to give the test persons consistent instructions through the complete test we designed a program that presented the instructions on a secondary screen.
+The instructions were a series of shapes equally to the shapes in the application buttons and the test persons where told to press the representative shape in the application as fast as they could to measure the reaction time.
+If they pressed the wrong button they where told to continue the test by pressing the right button, the application registered this as an IE.
+Each test were performed indoors with varying surroundings such as different lightning conditions and noise levels.
+We tested each version of the application on 5 persons all within the same age group (20-30) and with a variety of backgrounds.
+We had a gender split of 50\% women and 50\% men.
+In total we got 10 test results that we later analyzed against each other to measure if any differences in RTs or IEs between the two versions could be statistically confirmed.
 
 \subsection{Evaluation of the A/B test}
-This section will in short describe the evaluation process of the A/B test. How the test results were collected and what parameters we have had focus on during the test.
+Our test data received from the tests consisted of UNIX timestamps~\footnote{\url{http://www.unixtimestamp.com/}} in milliseconds.
+Each time the user interacted with the application it registered which button that was pressed and saved it together with a UNIX timestamp.
+Equally, every time the instruction program showed a new symbol it logged that together with a UNIX timestamp.
+As a result we received two data sets of symbols with corresponding timestamps for each test person, resulting in a total of approximately 400 records.
+Although the data were hard to interpret due to its compact look, a pyhton program were written to clean it up.
+We calculated each difference (RT) in time between when the instruction were given and when user interaction registered.
+Out of this we could calculate the mean RT for both groups LC and HC.
+The calculation of RT did not take in consideration if user input were a no match.
+We still considered it as an reaction.
+
+IEs were counted every time the user pressed a non matching object compared to the one given in the instructions.
+All IEs in each group, LC and HC, were counted to see if one of the groups produced more IEs.
 
 \section{Result}
-All results produced from the tests are here presented with clear numbers, conclusions and figures/graphics.
+From our results we can not draw any statistically significant differences in RT between the two groups HC and LC.
+This is most probably due to corrupt test data, a result from limitations in web application technology, see section \ref{sec:discussion}.
+With the IEs we found a significant difference between the groups.
 
-\subsection{Evaluation}
-The evaluation itself and a text about the evaluation results.
+\subsection{Reaction Times (RT)}
+asd
 
-\section{Discussion}
-In this section we will discuss the results from the tests. We will discuss what the results mean and how they should and could be interpreted.
+\subsection{Input Errors}
+asd
 
-\subsection{Conclusions and Guidelines}
-Here we will present our conclusions based on the resulting outcome from the tests.
-We will also present our four guidelines on how to design a touch interface compatible for emergency situations.
-These guidelines will be created based on the test results.
+\section{Discussion} \label{sec:discussion}
+In this section we will discuss the results from the tests. We will discuss what the results mean and how they should and could be interpreted. We are currently in the stage of analyzing our data.
 
-Below follows our guidelines that we have designed from our test results. The guidelines can be used when designing a
+\subsection{Drawbacks and Limitations} \label{subsec:drawbacks}
+One of the main drawbacks of this study is the limited number of test subjects.
+In order to get more credible result a larger group of test persons should be included.
+Preferable we should also had let the test persons do the test several of times to eliminate possible surrounding factors that could have affect the results.
 
-\subsection{Drawbacks and Limitations}
-This paper should not be used as a scientific foundation for any kind of argument.
-There are to many parameters affecting the results.
-Time limitation during the research period had a big influence on the credibility of the whole paper.
-We would like to emphasize some of the biggest drawbacks in the research and the paper by listing them below.
-\emph{Note that it is highly possible that there exists drawbacks not mentioned here}.
-
+Below is a asd
 \begin{description}
-	\item[Our group of test subjects was to small] To be able to get a more statistical valid result the test group has to be bigger.
-	\item[Possibly bad simulation of emergency situation] Due to the limited time reserved for this paper and its research a true simulation of an emergency situation could not be set.
-We did our best but it could had been done better.
-	\item[Many affecting parameters] The prototype is simple in its appearance but there are still many parameters that can affect the user interaction.
-Icons, icon size, optimal number of soft-buttons etc.
-All this, and more, should have been researched if done again.
+	\item[Our group of test subjects is to small] To be able to get a more statistical valid result the test group has to be bigger.
+	\item[Many affecting parameters] The prototype is simple in its appearance but there are still many parameters that can affect the users interaction and their RTs.
+Icons, icon size, optimal number of soft-buttons, size of hand-held device etc.
+All this, and more, should have been researched and taken into account if done again.
+	\item[Limited test environment] Our tests were made with using an Android smart-phone~\footnote{OnePlus two \url{https://oneplus.net/2}} system and the application were done using HTML5 and CSS3.
+We can not surely imply, without testing, that the same results would appear on an iPhone or any other smart-phone.
 \end{description}
@@
 \subsection{Future Work}
-Due to extremely limited time given for this paper there are many things that could be improved, made differently or simply just continued to be worked on.
-We have some concrete suggestions that could be a case for future work.
+Due to limited time given for this paper there are things that could be improved or just continued to be worked on. We have some concrete suggestions that could be a case for future work.
 
 \begin{itemize}
-	\item Extend the test group with more subjects. The patterns that slightly appeared in our results could with a bigger test group be more significant.
-	\item Make the same tests but with a better simulation of an emergency situation. Our proposal to this is to stage an emergent situation and make the test person interact with the complete situation.
+	\item Extend the test group with more test subjects.
+It is possible to think that the patterns that slightly appeared in our results will appear even more significant with a larger group of test subjects.
 	\item Our collected test data can be downloaded and used freely to investigate other aspect not mentioned in this paper.
 One proposal is to look at the different shapes and try to detect possible error patterns between them.
+Is the rhomb more frequently pressed wrongly compared to the other shapes?
+	\item Does our results apply on other systems and techniques?
+Our tests are limited to the Android system and a web application solution.
+It remains to answer if our results applies on all other systems.
+This is also a way of isolate some of all the affecting parameters mentioned in~\ref{subsec:drawbacks}.
 \end{itemize}

### 2015-11-04 data-parser.py

@@ -1,0 +1,54 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+# 
+# Author: Albin Hübsch - albin.hubsch@gmail.com
+# 
+
+# Import
+import os
+
+res = []
+
+# Fetch files in test resultat folder
+for file in os.listdir("./Testresultat"):
+	if file.endswith(".txt"):
+		fileA = file.split('-')
+		# print fileA
+		name = fileA[0]
+		dtype = fileA[1]
+
+		# print dtype
+
+		with open("./Testresultat/"+file) as f:
+			content = f.readlines()
+
+		cc = content[0].split(',')
+		cc.pop()
+
+
+		# shitstorm
+		if dtype == 'hc' or dtype == 'lc':
+			# pass
+			print dtype
+			# Parse data
+			for l in cc:
+				if '\n' in l:
+					print 'blöööö'
+				else:
+					shape = l.split(':')[0]
+					time = l.split(':')[1]
+
+					print name+','+shape+','+time
+					
+		elif dtype == 'instructions':
+			pass
+			# print dtype
+			# # Parse data
+			# for l in cc:
+			# 	if '\n' in l:
+			# 		print 'blöööö'
+			# 	else:
+			# 		shape = l.split(':')[0]
+			# 		time = l.split(':')[1]
+
+			# 		print name+','+shape+','+time

### 2015-11-04 Paper.tex
added results to paper

@@
 
+% Albins Packages
+\usepackage{array}
+
 \begin{document}
@@
 
-\title{Can a high color contrast touch interface increase user reaction time when using a smart phone web based application.}
+\title{Can a High Color Contrast Touch Interface Increase User Reaction Time when Using a Smart Phone Web Based Application.}
 
@@
 
-\titlerunning{Can high color contrast increase user reaction time}
+\titlerunning{Can High Color Contrast Increase User Reaction Time}
 
@@
 When this technology moves to a broader audience, higher demands on usability needs to be set~\cite{gong2004guidelines}.
-To further explore how usability can be improved using touch screen technology we are in this paper investigating if reaction time (referred to as RT in this paper) and user input errors (referred to as IE in this paper) can reach better results by increasing color contrast within the interface.
+To further explore how usability can be improved using touch screen technology we are in this paper investigating if reaction time (referred to as RT\footnote{Reaction Time: the time it takes for a user to react on instructions} in this paper) and user input errors (referred to as IE\footnote{Input Errors: the number of user input errors when interacting with a system} in this paper) can reach better results by increasing color contrast within the interface.
 Earlier work done in this field are exploring how we perceive different color contrast and how it can affect our reading performance~\cite{wu2003improving}.
@@
 Many best practices for Mobile development also shows that "requirements for sufficient color contrast"~\cite{marcus2013design} must be meet to best exaggerate the content.
-But still the question remains, if a high color contrast interface can increase the the RT\footnote{Reaction time: the time it takes for a user to react on instructions} and decrease user IE\footnote{Input errors: the number of user input errors when interacting with a system}.
+But still the question remains, if a high color contrast interface can increase the the RT and decrease user IE.
 
@@
 In order to be able to test if color contrast has an substantial impact on the RT and user IE of a touch user interface we have designed a simple web application for an Android smart-phone.
-The application exists in two versions, one with low color (LC) contrast and one with high color contrast (HC) as can be seen in Fig~\ref{fig:application}.
+The application exists in two versions, one with low color contrast (referred to as LC in this paper) and one with high color contrast (referred to as HC in this paper) as can be seen in Fig~\ref{fig:application}.
 
@@
 	\includegraphics[width=\textwidth]{application}
-	\caption{Our two color contrast versions of our application designed.\label{fig:application}}
+	\caption{Our two versions of the application designed with different color contrast.\label{fig:application}}
 \end{figure}
@@
 To be able to give the test persons consistent instructions through the complete test we designed a program that presented the instructions on a secondary screen.
-The instructions were a series of shapes equally to the shapes in the application buttons and the test persons where told to press the representative shape in the application as fast as they could to measure the reaction time.
+The instructions were a series (20) of shapes equally to the shapes in the application buttons and the test persons where told to press the representative shape in the application as fast as they could to measure the reaction time.
 If they pressed the wrong button they where told to continue the test by pressing the right button, the application registered this as an IE.
@@
 As a result we received two data sets of symbols with corresponding timestamps for each test person, resulting in a total of approximately 400 records.
-Although the data were hard to interpret due to its compact look, a pyhton program were written to clean it up.
+Although the data were hard to interpret due to its compact look, a python script were written to clean it up.
 We calculated each difference (RT) in time between when the instruction were given and when user interaction registered.
@@
 From our results we can not draw any statistically significant differences in RT between the two groups HC and LC.
-This is most probably due to corrupt test data, a result from limitations in web application technology, see section \ref{sec:discussion}.
-With the IEs we found a significant difference between the groups.
+This is most probably due to corrupt test data, a result from limitations in web application technology, see section \ref{subsec:drawbacks}.
+With IEs we found that the LC group produced significantly more IEs than the HC group.
 
 \subsection{Reaction Times (RT)}
-asd
+Table~\ref{tab:groupRT} shows our average RT and standard deviation for each group. According to the results people in HC had insignificant slower RTs compared to the ones in LC.
 
-\subsection{Input Errors}
-asd
+\begin{table}[]
+	\centering
+	\label{tab:groupRT}
+	\setlength{\tabcolsep}{1em}
+	\setlength\extrarowheight{1em}
+	\begin{tabular}{l|l|l}
+		\textbf{} & \textbf{Average RT} & \textbf{Standard Deviation} \\ \hline
+		\textbf{HC} & 782.69 ms & 968.67 ms \\ \hline
+		\textbf{LC} & 549.52 ms & 1393.03 ms
+	\end{tabular}
+	\caption{Average RT and standard deviation for each group, LC and HC.}
+\end{table}
+
+To validate that the groups RTs are insignificantly different we assumed the two data sets where normal distributed and performed a two tailed T-Test.
+The T-Test produced a p-value of 0.17 which is bigger than a desired error margin ($\alpha$) of 5\%.
+The T-Test is therefore proving that no differences in RT can be shown with our data.
+But regardless what the t-test says our standard deviations are hinting that something might be wrong with our data, please see section \ref{subsec:drawbacks}.
+
+\subsection{Input Errors (IE)}
+None of the groups where completely free from user IEs. As can be seen in table~\ref{tab:userIE} users that were given the LC interface produced 475\% more IEs than the HC group.
+
+\begin{table}[]
+	\centering
+	\label{tab:userIE}
+	\setlength{\tabcolsep}{1em}
+	\setlength\extrarowheight{1em}
+	\begin{tabular}{l|l|l|l}
+		\textbf{} & \textbf{Errors} & \textbf{Standard Deviation} & \textbf{Errors/User} \\ \hline
+		\textbf{HC} & 4 & 1.10 & 0.8 \\ \hline
+		\textbf{LC} & 19 & 3.49 & 3.8
+	\end{tabular}
+	\caption{Number of user IEs registered in each group and a calculation of IEs per user in each group}
+\end{table}
+
+Table~\ref{tab:userIE} shows us that there is a significant difference in number of IEs between the groups.
+The results also shows us that the users in the HC group had a more stable and consistent performance compared to LC group.
 
 \section{Discussion} \label{sec:discussion}
-In this section we will discuss the results from the tests. We will discuss what the results mean and how they should and could be interpreted. We are currently in the stage of analyzing our data.
+Our test results has shown that we can not increase the user reaction time by using a high color contrast interface when using a smart phone web based application.
+However we could see that the high color contrast interface was more reliable in performance when it comes to the amount of user input errors.
+This is fact according to our results.
+But what we have seen in our collected test data can strongly negotiate the legibility of the results.
 
 \subsection{Drawbacks and Limitations} \label{subsec:drawbacks}
+TODO
+	- Diskutera problemet med testdatan och tekniska begränsningar
+
 One of the main drawbacks of this study is the limited number of test subjects.

### 2015-11-06 Paper.tex
Final draft

@@
 	\includegraphics[width=\textwidth]{application}
-	\caption{Our two versions of the application designed with different color contrast.\label{fig:application}}
+	\caption{Our two versions of the application designed with different color contrast.
+	\label{fig:application}}
 \end{figure}
 
-We designed the application by following design guidelines given here~\cite{hoober2011designing} and~\cite{johnson2013designing}.
+We designed the application by following design guidelines given here~\cite{hoober2011designing}~\cite{johnson2013designing}~\cite{gong2004guidelines}~\cite{norman2013design}.
 
@@
 
-The application consists of 4 buttons~\footnote{On screen button}, each button representing a function.
+The application consists of 4 buttons\footnote{On screen button}, each button representing a function.
 To fraction each button from the others we put a unique shape in each button.
@@
 To be able to give the test persons consistent instructions through the complete test we designed a program that presented the instructions on a secondary screen. 
-The instructions were a series (20) of shapes equally to the shapes in the application buttons and the test persons where told to press the representative shape in the application as fast as they could to measure the reaction time.
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{instructions}
+	\caption{Our program designed to present user instructions.
+	\label{fig:instructions}}
+\end{figure}
+The instructions was a series of 20 instructions with shapes equally to the shapes in the application buttons.
+The test persons where told to press the representative shape in the application as fast as they could to measure the reaction time.
 If they pressed the wrong button they where told to continue the test by pressing the right button, the application registered this as an IE.
@@
 We had a gender split of 50\% women and 50\% men.
-In total we got 10 test results that we later analyzed against each other to measure if any differences in RTs or IEs between the two versions could be statistically confirmed.
+In total we got 10 test results that we later grouped into LC and HC.
+We analyzed them against each other to measure if any differences in RTs or IEs between the two versions could be statistically confirmed.
 
 \subsection{Evaluation of the A/B test}
-Our test data received from the tests consisted of UNIX timestamps~\footnote{\url{http://www.unixtimestamp.com/}} in milliseconds.
+Our test data received from the tests consisted of UNIX timestamps\footnote{\url{http://www.unixtimestamp.com/}} in milliseconds.
 Each time the user interacted with the application it registered which button that was pressed and saved it together with a UNIX timestamp.
@@
 From our results we can not draw any statistically significant differences in RT between the two groups HC and LC.
-This is most probably due to corrupt test data, a result from limitations in web application technology, see section \ref{subsec:drawbacks}.
+This is most probably due to corrupt test data, a result from limitations in web application technology, see section \ref{subsec:discussion}.
 With IEs we found that the LC group produced significantly more IEs than the HC group.
@@
 The T-Test is therefore proving that no differences in RT can be shown with our data.
-But regardless what the t-test says our standard deviations are hinting that something might be wrong with our data, please see section \ref{subsec:drawbacks}.
+But regardless what the t-test says our standard deviations are hinting that something might be wrong with our data, please see section \ref{subsec:discussion}.
 
@@
 Table~\ref{tab:userIE} shows us that there is a significant difference in number of IEs between the groups.
-The results also shows us that the users in the HC group had a more stable and consistent performance compared to LC group.
+The results also show us that the users in the HC group generally performed more stable and consistent compared to the LC group.
 
-\section{Discussion} \label{sec:discussion}
+\section{Discussion}\label{sec:discussion}
 Our test results has shown that we can not increase the user reaction time by using a high color contrast interface when using a smart phone web based application.
@@
 But what we have seen in our collected test data can strongly negotiate the legibility of the results.
+The calculated standard deviations gave us hints on that something were wrong so we dug deeper into each test persons results and found that the data must be corrupt.
+We found that we randomly receive negative RTs which in theory should be completely impossible.
+We were prepared that the timestamps could be off sync with each others but that would be easy to compensate.
+Here we got inconsistent hick ups in our timestamps.
+We suspect this is a result from either hardware limitations or limitations in the JavaScript\footnote{A prototype based dynamic scripting language} engine for web applications on android.
 
-\subsection{Drawbacks and Limitations} \label{subsec:drawbacks}
-TODO
-	- Diskutera problemet med testdatan och tekniska begränsningar
+As for this our conclusion is that HC interfaces are the preferred method to design interfaces as they deliver a more stable user interaction pattern.
+Apart from this, smart phone web based applications should only be used if, sometimes slow technology, user input errors and long reaction times from the user can be accepted.
 
-One of the main drawbacks of this study is the limited number of test subjects.
-In order to get more credible result a larger group of test persons should be included.
-Preferable we should also had let the test persons do the test several of times to eliminate possible surrounding factors that could have affect the results.
+\subsection{Drawbacks and Limitations}\label{subsec:drawbacks}
+The main drawback of this study is the corrupt data set.
+We have to have this in mind when we draw any conclusions out of the results.
+This problem could be solved by simply rerun the whole test using a native smart phone application instead of a web based solution.
 
-Below is a asd
+Another drawback worth to mention is that, preferable we should also have had let the test persons do the test several number of times in order to eliminate possible surrounding factors that could have affected the results.
+We should also had let some of the test persons perform tests with both the LC and HC versions in order to see how fast they memorize patterns.
+
+Further are some more drawbacks and limitations that we would like to mention.
 \begin{description}
 	\item[Our group of test subjects is to small] To be able to get a more statistical valid result the test group has to be bigger.
+In this paper we also only assumed it was normal distributed, not tested.
 	\item[Many affecting parameters] The prototype is simple in its appearance but there are still many parameters that can affect the users interaction and their RTs.
@@
 All this, and more, should have been researched and taken into account if done again.
-	\item[Limited test environment] Our tests were made with using an Android smart-phone~\footnote{OnePlus two \url{https://oneplus.net/2}} system and the application were done using HTML5 and CSS3.
-We can not surely imply, without testing, that the same results would appear on an iPhone or any other smart-phone.
+	\item[Limited test environment] Our tests were made using an Android based smart-phone\footnote{OnePlus two \url{https://oneplus.net/2}} system and the application were made using HTML5\footnote{HyperText Markup Language, markup standard for WWW}, CSS3\footnote{Cascading Style Sheet, styling standard for WWW} and JavaScript.
+We can not surely imply, without testing, that the same results would appear on an iPhone or any other smart-phone or even with a native application.
 \end{description}
@@
 \subsection{Future Work}
-Due to limited time given for this paper there are things that could be improved or just continued to be worked on. We have some concrete suggestions that could be a case for future work.
+Due to the failed data set that we received in this paper there are things that could be improved or continued to be worked on. 
+We do have some concrete suggestions that could be case for future work.
 
 \begin{itemize}
+	\item Do tests using a native application.
 	\item Extend the test group with more test subjects.
 It is possible to think that the patterns that slightly appeared in our results will appear even more significant with a larger group of test subjects.
-	\item Our collected test data can be downloaded and used freely to investigate other aspect not mentioned in this paper.
+	\item Our collected test data can be downloaded and used freely to investigate other aspects not mentioned in this paper.
 One proposal is to look at the different shapes and try to detect possible error patterns between them.
-Is the rhomb more frequently pressed wrongly compared to the other shapes?
+Is the rhomb more frequently a case for IE compared to the other shapes?
 	\item Does our results apply on other systems and techniques?
-Our tests are limited to the Android system and a web application solution.
+Our tests are limited to the Android system and a web based application solution.
 It remains to answer if our results applies on all other systems.
-This is also a way of isolate some of all the affecting parameters mentioned in~\ref{subsec:drawbacks}.
+This is also a way of isolating some of the affecting parameters mentioned in~\ref{subsec:drawbacks}.
 \end{itemize}
+
+\section{Acknowledgments}
+The author would like to thank the peer reviewers who provided great valuable comments on both the content and structure of this paper.
 
@@
 %
-\nocite{*}  % Includes ALL entries from the .bib-file, even if they are
+% \nocite{*}  % Includes ALL entries from the .bib-file, even if they are
             % not '\cite{}'-ed in the text above

### 2015-11-17 Paper.tex
Updates to final paper

@@
 The main goal with this paper is to evaluate if color contrast has a significant impact on usability in web based smart-phone applications.
-Consumer touch screen devices such as smart-phones has rapidly increased in amount and availability recent years.
-The touch screen technology have made great advances ~\cite{jennings2013touch} and it is more frequently used as a way of receiving user input.
+Consumer touch screen devices such as smart-phones have rapidly increased in amount and availability recent years.
+The touch screen technology have made great advances~\cite{jennings2013touch} and it is frequently used as a way of receiving user input.
 When this technology moves to a broader audience, higher demands on usability needs to be set~\cite{gong2004guidelines}.
-To further explore how usability can be improved using touch screen technology we are in this paper investigating if reaction time (referred to as RT\footnote{Reaction Time: the time it takes for a user to react on instructions} in this paper) and user input errors (referred to as IE\footnote{Input Errors: the number of user input errors when interacting with a system} in this paper) can reach better results by increasing color contrast within the interface.
-Earlier work done in this field are exploring how we perceive different color contrast and how it can affect our reading performance~\cite{wu2003improving}.
-It has also been proved that Chromaticity, Contrast, and Cone Opponency in color space can affect RTs~\cite{mckeefry2003simple}.
-Many best practices for Mobile development also shows that "requirements for sufficient color contrast"~\cite{marcus2013design} must be meet to best exaggerate the content.
+To further explore how usability can be improved using touch screen technology we have in this paper investigated if reaction time (the time it takes for a user to react on instructions, further referred to as RT in this paper) and user input errors (the number of user input errors when interacting with a system, further referred to as UIE in this paper) can reach better results by increasing color contrast within the interface.
+Better results are assumed as faster RTs and less number of UIEs.
+
+Earlier studies completed in this field has explored how we perceive different color contrast and how it can affect our reading performance~\cite{wu2003improving}.
+It has also been proved that chromaticity, contrast, and cone opponency in color space can affect RTs~\cite{mckeefry2003simple}.
+Many best practices for Mobile development have also shown that "requirements for sufficient color contrast"~\cite{marcus2013design} must be meet to best exaggerate the content.
 But still the question remains, if a high color contrast interface can increase the the RT and decrease user IE.
 
-High RTs and low user IE are especially desirable when designing user interfaces for situations with high demands on quick user input and low error tolerance such as emergency situations.
+High RTs and low user IE are especially desirable when designing user interfaces for situations with high demands on quick user input and low error tolerance such as in emergency situations.
 The results of this paper can be used by any designer or developer.
@@
 In order to be able to test if color contrast has an substantial impact on the RT and user IE of a touch user interface we have designed a simple web application for an Android smart-phone.
-The application exists in two versions, one with low color contrast (referred to as LC in this paper) and one with high color contrast (referred to as HC in this paper) as can be seen in Fig~\ref{fig:application}.
+The application exists in two versions, one with low color contrast (referred to as LCC in this paper) and one with high color contrast (referred to as HCC in this paper) as can be seen in Fig~\ref{fig:application}.
 
@@
 We designed the application by following design guidelines given here~\cite{hoober2011designing}~\cite{johnson2013designing}~\cite{gong2004guidelines}~\cite{norman2013design}.
+These guidelines can be seen as a set of rules to follow when designing any kind of user interface.
 
 \subsection{Designing the A/B test}
-We conducted an A/B test to measure the differences in RT and IE between the two versions.
+We conducted an A/B test to measure the differences in RT and UIE between the two versions.
 An A/B test is a commonly used method by developers and designers to test differences in performance between applications when the differentiated factors are known~\cite{johnson2013designing}.
-As in this case our known factor is the contrast difference.
+Where in this case our known factor is the contrast difference.
 
 The application consists of 4 buttons\footnote{On screen button}, each button representing a function.
-To fraction each button from the others we put a unique shape in each button.
-The shapes we used are a, square, circle, triangle and a rhomb~\ref{fig:application}.
+To differentiate each button from the others we put a unique shape in each button.
+The shapes we used where a, square, circle, triangle and a rhomb (Fig~\ref{fig:application}).
 
@@
 We calculated each difference (RT) in time between when the instruction were given and when user interaction registered.
-Out of this we could calculate the mean RT for both groups LC and HC.
+Out of this we could calculate the mean RT for both groups LCC and HCC.
 The calculation of RT did not take in consideration if user input were a no match.

### 2015-11-20 Paper.tex
corrections

@@
 \section{Method}
-In order to be able to test if color contrast has an substantial impact on the RT and user IE of a touch user interface we have designed a simple web application for an Android smart-phone.
+In order to be able to test if color contrast has a substantial impact on the RT and UIE of a touch user interface we have designed a simple web application for an Android smart-phone.
 The application exists in two versions, one with low color contrast (referred to as LCC in this paper) and one with high color contrast (referred to as HCC in this paper) as can be seen in Fig~\ref{fig:application}.
+We conducted an A/B test to measure the performance between the versions.
 
@@
 These guidelines can be seen as a set of rules to follow when designing any kind of user interface.
+We used guidelines to get proper sized buttons, good spacing between content and best positioning of navigation.
 
@@
 \end{figure}
-The instructions was a series of 20 instructions with shapes equally to the shapes in the application buttons.
-The test persons where told to press the representative shape in the application as fast as they could to measure the reaction time.
-If they pressed the wrong button they where told to continue the test by pressing the right button, the application registered this as an IE.
-Each test were performed indoors with varying surroundings such as different lightning conditions and noise levels.
-We tested each version of the application on 5 persons all within the same age group (20-30) and with a variety of backgrounds.
-We had a gender split of 50\% women and 50\% men.
-In total we got 10 test results that we later grouped into LC and HC.
-We analyzed them against each other to measure if any differences in RTs or IEs between the two versions could be statistically confirmed.
+The instructions were a series of 20 instructions with shapes equal to the shapes in the application buttons.
+The test persons were told to press the representative shape in the application as fast as they could in order to measure the reaction time.
+If they pressed the wrong button they were told to continue the test by pressing the right button, the application registered this as an UIE.
+Each test was performed indoors with varying surroundings such as different lightning conditions and noise levels.
+We tested each version of the application on 5 persons, all within the same age group (20-30) and with a variety of backgrounds.
+In total we got 10 test results with a gender split of 50\% women and 50\% men that we later grouped into LCC and HCC.
+We analyzed them against each other to measure if any differences in RT or UIE between the two versions could be statistically confirmed.
 
 \subsection{Evaluation of the A/B test}
-Our test data received from the tests consisted of UNIX timestamps\footnote{\url{http://www.unixtimestamp.com/}} in milliseconds.
+Our test data received from the tests consisted of UNIX timestamps\footnote{More info at: \url{http://www.unixtimestamp.com/}} in milliseconds.
 Each time the user interacted with the application it registered which button that was pressed and saved it together with a UNIX timestamp.
-Equally, every time the instruction program showed a new symbol it logged that together with a UNIX timestamp.
+Equally, every time the instruction program showed a new symbol it logged the symbol together with a UNIX timestamp.
 As a result we received two data sets of symbols with corresponding timestamps for each test person, resulting in a total of approximately 400 records.
-Although the data were hard to interpret due to its compact look, a python script were written to clean it up.
-We calculated each difference (RT) in time between when the instruction were given and when user interaction registered.
+Although the data was hard to interpret due to its compact look, a python script was written to structure the resulting timestamps into a more readable format.
+We calculated each difference (RT) in time between when the instruction was given and when user interaction registered.
 Out of this we could calculate the mean RT for both groups LCC and HCC.
-The calculation of RT did not take in consideration if user input were a no match.
-We still considered it as an reaction.
+The calculation of RT did not take in consideration if user input was a no match.
+It was still considered as an reaction.
 
 IEs were counted every time the user pressed a non matching object compared to the one given in the instructions.
-All IEs in each group, LC and HC, were counted to see if one of the groups produced more IEs.
+All IEs in each group, LCC and HCC, were counted to see if one of the groups produced more UIEs.
 
 \section{Result}
-From our results we can not draw any statistically significant differences in RT between the two groups HC and LC.
-This is most probably due to corrupt test data, a result from limitations in web application technology, see section \ref{subsec:discussion}.
-With IEs we found that the LC group produced significantly more IEs than the HC group.
+From our results we can not draw any statistically significant differences in reaction time between the two groups high color contrast and low color contrast.
+This is most probably due to corrupt test data, a result from limitations in web application technology, see section \ref{sec:discussion}.
+With user input errors we found that the low color contrast group produced significantly more user input errors than the hight color contrast group.
 
 \subsection{Reaction Times (RT)}
-Table~\ref{tab:groupRT} shows our average RT and standard deviation for each group. According to the results people in HC had insignificant slower RTs compared to the ones in LC.
+Table~\ref{tab:groupRT} shows our average RT and standard deviation for each group. According to the results people in HCC had insignificant slower RTs compared to the ones in LCC.
 
@@
 	\centering
-	\label{tab:groupRT}
 	\setlength{\tabcolsep}{1em}
@@
 		\textbf{} & \textbf{Average RT} & \textbf{Standard Deviation} \\ \hline
-		\textbf{HC} & 782.69 ms & 968.67 ms \\ \hline
-		\textbf{LC} & 549.52 ms & 1393.03 ms
+		\textbf{HC} & 783 ms & 969 ms \\ \hline
+		\textbf{LC} & 550 ms & 1393 ms
 	\end{tabular}
-	\caption{Average RT and standard deviation for each group, LC and HC.}
+	\caption{Average reaction time and the standard deviation for each group, low color contrast and high color contrast.}
+	\label{tab:groupRT}
 \end{table}
@@
 The T-Test produced a p-value of 0.17 which is bigger than a desired error margin ($\alpha$) of 5\%.
-The T-Test is therefore proving that no differences in RT can be shown with our data.
-But regardless what the t-test says our standard deviations are hinting that something might be wrong with our data, please see section \ref{subsec:discussion}.
+The T-Test is therefore proving that no differences in RT exists within our data.
+But regardless what the t-test says our standard deviations are hinting that something might be wrong with our data (see section \ref{sec:discussion}).
 
 \subsection{Input Errors (IE)}
-None of the groups where completely free from user IEs. As can be seen in table~\ref{tab:userIE} users that were given the LC interface produced 475\% more IEs than the HC group.
+None of the groups where completely free from user input errors. As can be seen in table~\ref{tab:userIE} users that were given the LCC interface produced 475\% more UIE than the HCC group.
 
@@
 	\centering
-	\label{tab:userIE}
 	\setlength{\tabcolsep}{1em}
@@
 	\caption{Number of user IEs registered in each group and a calculation of IEs per user in each group}
+	\label{tab:userIE}
 \end{table}
 
-Table~\ref{tab:userIE} shows us that there is a significant difference in number of IEs between the groups.
-The results also show us that the users in the HC group generally performed more stable and consistent compared to the LC group.
+Table~\ref{tab:userIE} shows us that the users in the HCC group generally had a more stable and consistent performance compared to the LCC group.
+We also performed a two tailed t-test on the UIE data set.
+The outcome of this test was a p-value of 0.001 which is significantly smaller than a $\alpha$ of 5\% telling us that the HCC group performed better.
 
 \section{Discussion}\label{sec:discussion}
-Our test results has shown that we can not increase the user reaction time by using a high color contrast interface when using a smart phone web based application.
-However we could see that the high color contrast interface was more reliable in performance when it comes to the amount of user input errors.
-This is fact according to our results.
-But what we have seen in our collected test data can strongly negotiate the legibility of the results.
-The calculated standard deviations gave us hints on that something were wrong so we dug deeper into each test persons results and found that the data must be corrupt.
-We found that we randomly receive negative RTs which in theory should be completely impossible.
-We were prepared that the timestamps could be off sync with each others but that would be easy to compensate.
-Here we got inconsistent hick ups in our timestamps.
-We suspect this is a result from either hardware limitations or limitations in the JavaScript\footnote{A prototype based dynamic scripting language} engine for web applications on android.
+Our test results have shown that we can not increase the user reaction time by using a high color contrast interface when using a smart phone web based application.
+However we could see that the high color contrast interface was more reliable in performance when it comes to the amount of user input errors, according to our results.
+What we have seen in our collected test data can strongly negotiate the legibility of the results.
+The calculated standard deviations gave us hints on that something was wrong.
+We dug deeper into each test persons results and found that the data must be corrupt.
+We found that we had randomly received negative RTs which in theory should be completely impossible.
+We were prepared that the timestamps could be off sync due to individual system clocks and no boot pairing.
+This would have resulted in a consistent off sync.
+Instead we got inconsistent hick ups in our timestamps.
+We suspect this is a result from either hardware limitations or limitations in the JavaScript\footnote{A prototype based dynamic scripting language} engine for web applications on Android.
 
@@
 The main drawback of this study is the corrupt data set.
-We have to have this in mind when we draw any conclusions out of the results.
-This problem could be solved by simply rerun the whole test using a native smart phone application instead of a web based solution.
+Something to have in mind when we draw any conclusions out of the results.
+This problem could be solved by simply rerunning the whole test using a native smart phone application instead of a web based solution.
 
-Another drawback worth to mention is that, preferable we should also have had let the test persons do the test several number of times in order to eliminate possible surrounding factors that could have affected the results.
-We should also had let some of the test persons perform tests with both the LC and HC versions in order to see how fast they memorize patterns.
+Each test person performed only one test with a supervisory selected interface, the LCC or HCC version.
+To eliminate possible affecting surrounding factors each person should have done the test several times and with both the LCC and HCC interfaces.
+This would also have made it possible to recognize if the test persons memorized the patterns in any way.
 
-Further are some more drawbacks and limitations that we would like to mention.
 \begin{description}
-	\item[Our group of test subjects is to small] To be able to get a more statistical valid result the test group has to be bigger.
-In this paper we also only assumed it was normal distributed, not tested.
+	\item[Small test group] To be able to get a more statistical valid result the test group has to be bigger. In this paper we also only assumed it was normal distributed, we did not test it.
 	\item[Many affecting parameters] The prototype is simple in its appearance but there are still many parameters that can affect the users interaction and their RTs.
@@
 All this, and more, should have been researched and taken into account if done again.
-	\item[Limited test environment] Our tests were made using an Android based smart-phone\footnote{OnePlus two \url{https://oneplus.net/2}} system and the application were made using HTML5\footnote{HyperText Markup Language, markup standard for WWW}, CSS3\footnote{Cascading Style Sheet, styling standard for WWW} and JavaScript.
+	\item[Limited test environment] Our tests were made using an Android based smart-phone\footnote{OnePlus Two \url{https://oneplus.net/2}} system and the application were made using HTML5\footnote{HyperText Markup Language, markup standard for WWW}, CSS3\footnote{Cascading Style Sheet, styling standard for WWW} and JavaScript.
 We can not surely imply, without testing, that the same results would appear on an iPhone or any other smart-phone or even with a native application.
@@
 \begin{itemize}
-	\item Do tests using a native application.
+	\item Perform tests using a native application.
 	\item Extend the test group with more test subjects.
@@
 Is the rhomb more frequently a case for IE compared to the other shapes?
-	\item Does our results apply on other systems and techniques?
+	\item Do our results apply on other systems and techniques?
 Our tests are limited to the Android system and a web based application solution.
@@
 \section{Acknowledgments}
-The author would like to thank the peer reviewers who provided great valuable comments on both the content and structure of this paper.
+The author would like to thank the peer reviewers who provided valuable comments on both the content and structure of this paper.
 

### 2015-11-21 Paper.tex
Corrections, adds and deletions

@@
 \begin{abstract}
-Here goes paper abstract
+This study aims to investigate if there is a performance difference between a high color contrast and a low color contrast touch screen interface.
+The performance was measured by combining the time each test subject took to respond on instructions (reaction time) and the number of input errors.
+The result shows that the high color contrast interface resulted in significantly fewer user input errors.
+There was no differences in reaction time between the two interfaces.
 \end{abstract}
 %
+%
+This study aims to investigate if it is possible to receive better user performance when using a high color contrast compared to a low color contrast touch screen interface.
+The performance was measured by combining the time each user took to respond on instructions (reaction time) and the number of input errors from the user.
+Our result shows that the low color contrast interface produced 475\% more user input errors compared to the high color contrast interface.
+No difference in reaction time could be found between the two versions.
 %%%%% END OF 2nd ADJUSTMENTS SECTION %%%%%
@@
 It has also been proved that chromaticity, contrast, and cone opponency in color space can affect RTs~\cite{mckeefry2003simple}.
-Many best practices for Mobile development have also shown that "requirements for sufficient color contrast"~\cite{marcus2013design} must be meet to best exaggerate the content.
-But still the question remains, if a high color contrast interface can increase the the RT and decrease user IE.
+Many best practices for Mobile development have also shown that "requirements for sufficient color contrast"~\cite{marcus2013design} must be met to best exaggerate the content.
+Still the question remains, can a high color contrast interface increase the the RT and decrease UIE?
 
@@
 \section{Method}
-In order to be able to test if color contrast has a substantial impact on the RT and UIE of a touch user interface we have designed a simple web application for an Android smart-phone.
+In order to be able to test if color contrast has a substantial impact on the RT and UIE of a touch screen user interface we have designed a simple web application for an Android smart-phone.
 The application exists in two versions, one with low color contrast (referred to as LCC in this paper) and one with high color contrast (referred to as HCC in this paper) as can be seen in Fig~\ref{fig:application}.
@@
 To differentiate each button from the others we put a unique shape in each button.
-The shapes we used where a, square, circle, triangle and a rhomb (Fig~\ref{fig:application}).
+The shapes we used were a, square, circle, triangle and a rhomb (Fig~\ref{fig:application}).
 
@@
 \end{figure}
-The instructions were a series of 20 instructions with shapes equal to the shapes in the application buttons.
+The instructions were a series of 20 instructions with shapes identical to the ones in the application buttons.
 The test persons were told to press the representative shape in the application as fast as they could in order to measure the reaction time.
@@
 Each test was performed indoors with varying surroundings such as different lightning conditions and noise levels.
+
 We tested each version of the application on 5 persons, all within the same age group (20-30) and with a variety of backgrounds.
@@
 \subsection{Evaluation of the A/B test}
-Our test data received from the tests consisted of UNIX timestamps\footnote{More info at: \url{http://www.unixtimestamp.com/}} in milliseconds.
+Our data received from the tests consisted of UNIX timestamps\footnote{More info at: \url{http://www.unixtimestamp.com/}} measured in milliseconds.
 Each time the user interacted with the application it registered which button that was pressed and saved it together with a UNIX timestamp.
 Equally, every time the instruction program showed a new symbol it logged the symbol together with a UNIX timestamp.
-As a result we received two data sets of symbols with corresponding timestamps for each test person, resulting in a total of approximately 400 records.
+As a result we received two data sets of symbols with corresponding timestamps for each test person, resulting in a total of 200 records.
 Although the data was hard to interpret due to its compact look, a python script was written to structure the resulting timestamps into a more readable format.
-We calculated each difference (RT) in time between when the instruction was given and when user interaction registered.
+We calculated each RT by subtracting the timestamp when the instruction was given from the registered user input timestamp.
 Out of this we could calculate the mean RT for both groups LCC and HCC.
@@
 
-IEs were counted every time the user pressed a non matching object compared to the one given in the instructions.
+UIEs were counted every time the user pressed a non matching object compared to the one given in the instructions.
 All IEs in each group, LCC and HCC, were counted to see if one of the groups produced more UIEs.
@@
 
-To validate that the groups RTs are insignificantly different we assumed the two data sets where normal distributed and performed a two tailed T-Test.
+To validate that the groups RTs are insignificantly different we assumed the two data sets where normal distributed based on the n>30 rule, and performed a two tailed T-Test.
 The T-Test produced a p-value of 0.17 which is bigger than a desired error margin ($\alpha$) of 5\%.
@@
 \subsection{Input Errors (IE)}
-None of the groups where completely free from user input errors. As can be seen in table~\ref{tab:userIE} users that were given the LCC interface produced 475\% more UIE than the HCC group.
+None of the groups where completely free from user input errors. As can be seen in table~\ref{tab:userIE}, users that were given the LCC interface produced 475\% more UIE than the HCC group.
 
@@
 
-As for this our conclusion is that HC interfaces are the preferred method to design interfaces as they deliver a more stable user interaction pattern.
-Apart from this, smart phone web based applications should only be used if, sometimes slow technology, user input errors and long reaction times from the user can be accepted.
+Our conclusion is that HCC interfaces are the preferred method to design interfaces as they deliver a more stable user interaction pattern.
+Apart from this, smart phone web based applications should only be used if sometimes slow technology, user input errors and long reaction times from the user can be accepted.
 
@@
 \begin{description}
-	\item[Small test group] To be able to get a more statistical valid result the test group has to be bigger. In this paper we also only assumed it was normal distributed, we did not test it.
-	\item[Many affecting parameters] The prototype is simple in its appearance but there are still many parameters that can affect the users interaction and their RTs.
-Icons, icon size, optimal number of soft-buttons, size of hand-held device etc.
+	\item[Small test group.] To be able to get a more statistical valid result the test group has to be bigger.
+	\item[Many affecting parameters.] The prototype is simple in its appearance but there are still many parameters that can affect the users interaction and their RTs.
+Icons, icon size, optimal number of on screen buttons, size of hand-held device etc.
 All this, and more, should have been researched and taken into account if done again.
-	\item[Limited test environment] Our tests were made using an Android based smart-phone\footnote{OnePlus Two \url{https://oneplus.net/2}} system and the application were made using HTML5\footnote{HyperText Markup Language, markup standard for WWW}, CSS3\footnote{Cascading Style Sheet, styling standard for WWW} and JavaScript.
+	\item[Limited test environment.] Our tests were made using an Android based smart-phone\footnote{OnePlus Two \url{https://oneplus.net/2}} and the application were made using HTML5\footnote{HyperText Markup Language, markup standard for WWW}, CSS3\footnote{Cascading Style Sheet, styling standard for WWW} and JavaScript.
 We can not surely imply, without testing, that the same results would appear on an iPhone or any other smart-phone or even with a native application.

### 2015-11-23 Paper.tex
Corrections, adds and deletions

@@
 
+%
 \begin{document}
@@
 \begin{abstract}
-This study aims to investigate if there is a performance difference between a high color contrast and a low color contrast touch screen interface.
+This study aims to investigate if it is possible to receive better user performance when using a high color contrast compared to a low color contrast touch screen interface in a mobile web application.
+The performance was measured by combining the time each user took to respond to instructions (reaction time) and the number of input errors from the user.
+Our result shows that the low color contrast interface produced 475\% more user input errors compared to the high color contrast interface.
+No difference in reaction time could be found between the two versions.
+\end{abstract}
+%
+%
+%This study aims to investigate if there is a performance difference between a high color contrast and a low color contrast touch screen interface.
 The performance was measured by combining the time each test subject took to respond on instructions (reaction time) and the number of input errors.
@@
 There was no differences in reaction time between the two interfaces.
-\end{abstract}
-%
-%
-This study aims to investigate if it is possible to receive better user performance when using a high color contrast compared to a low color contrast touch screen interface.
-The performance was measured by combining the time each user took to respond on instructions (reaction time) and the number of input errors from the user.
-Our result shows that the low color contrast interface produced 475\% more user input errors compared to the high color contrast interface.
-No difference in reaction time could be found between the two versions.
 %%%%% END OF 2nd ADJUSTMENTS SECTION %%%%%
@@
 	\caption{Our two versions of the application designed with different color contrast.
+To the left the low color contrast interface and to the right the high color contrast interface.
+The application and its interface was designed specifically for this test.
 	\label{fig:application}}
@@
 	\caption{Our program designed to present user instructions.
+Instructions were given in a series of 20.
+Between each instruction there was a delay set to be between 2.5 - 4 seconds.
+Each time a new symbol where showed a timestamp were logged in a unique user instruction file.
 	\label{fig:instructions}}
@@
 	\end{tabular}
-	\caption{Average reaction time and the standard deviation for each group, low color contrast and high color contrast.}
-	\label{tab:groupRT}
+	\caption{Average reaction time and standard deviation for each group, low color contrast and high color contrast.
+A two tailed t-test was performed on the two groups and showed that no significant difference could be determined between them.
+	\label{tab:groupRT}}
 \end{table}
@@
 The T-Test is therefore proving that no differences in RT exists within our data.
-But regardless what the t-test says our standard deviations are hinting that something might be wrong with our data (see section \ref{sec:discussion}).
+Regardless what the t-test says our standard deviations are indicating that something might be wrong with our data (see section \ref{sec:discussion}).
 
@@
 	\end{tabular}
-	\caption{Number of user IEs registered in each group and a calculation of IEs per user in each group}
-	\label{tab:userIE}
+	\caption{Number of user input errors registered in each group and a calculation of IEs per user in each group.
+The low color contrast interface produced 475\% more UIE compared to the high color contrast version.
+A two tailed t-test also showed that there is a significant difference between the two versions.
+A high color contrast interface can therefore be a preferred design method if a low amount of user input errors is desired.
+	\label{tab:userIE}}
 \end{table}

### 2015-11-23 Paper.tex
corrections

@@
 	Umeå University, Sweden \\
-	\email{id11ahh@cs.umu.se}
+	\email{albin.hubsch@gmail.com} \\
+	\url{http://albinhubsch.se}
 }
@@
 Many best practices for Mobile development have also shown that "requirements for sufficient color contrast"~\cite{marcus2013design} must be met to best exaggerate the content.
-Still the question remains, can a high color contrast interface increase the the RT and decrease UIE?
+Still the question remains, can a high color contrast interface increase the the reaction time and decrease the amount of user input errors?
 
-High RTs and low user IE are especially desirable when designing user interfaces for situations with high demands on quick user input and low error tolerance such as in emergency situations.
+High RTs and low UIEs are especially desirable when designing user interfaces for situations with high demands on quick user input and low error tolerance such as in emergency situations.
 The results of this paper can be used by any designer or developer.
@@
 In order to be able to test if color contrast has a substantial impact on the RT and UIE of a touch screen user interface we have designed a simple web application for an Android smart-phone.
-The application exists in two versions, one with low color contrast (referred to as LCC in this paper) and one with high color contrast (referred to as HCC in this paper) as can be seen in Fig~\ref{fig:application}.
+The application exists in two versions, one with low color contrast (referred to as LCC in this paper) and one with high color contrast (referred to as HCC in this paper) interface as can be seen in Fig~\ref{fig:application}.
 We conducted an A/B test to measure the performance between the versions.
@@
 We tested each version of the application on 5 persons, all within the same age group (20-30) and with a variety of backgrounds.
-In total we got 10 test results with a gender split of 50\% women and 50\% men that we later grouped into LCC and HCC.
+In total we got 10 test results with a gender split of 50\% women and 50\% men that grouped into LCC and HCC.
 We analyzed them against each other to measure if any differences in RT or UIE between the two versions could be statistically confirmed.
@@
 Out of this we could calculate the mean RT for both groups LCC and HCC.
-The calculation of RT did not take in consideration if user input was a no match.
+The calculation of RT did not take in consideration if user input was a match with the instruction or not.
 It was still considered as an reaction.
@@
 UIEs were counted every time the user pressed a non matching object compared to the one given in the instructions.
-All IEs in each group, LCC and HCC, were counted to see if one of the groups produced more UIEs.
+All input errors in each group, LCC and HCC, were counted to see if one of the groups produced more UIEs.
 
@@
 \subsection{Reaction Times (RT)}
-Table~\ref{tab:groupRT} shows our average RT and standard deviation for each group. According to the results people in HCC had insignificant slower RTs compared to the ones in LCC.
+Table~\ref{tab:groupRT} shows our average reaction time and standard deviation for each group.
+According to the results people in the high color contrast group had insignificant slower reaction times compared to the ones in the low color contrast group.
 
@@
 		\textbf{} & \textbf{Average RT} & \textbf{Standard Deviation} \\ \hline
-		\textbf{HC} & 783 ms & 969 ms \\ \hline
-		\textbf{LC} & 550 ms & 1393 ms
+		\textbf{HCC} & 783 ms & 969 ms \\ \hline
+		\textbf{LCC} & 550 ms & 1393 ms
 	\end{tabular}
@@
 
-To validate that the groups RTs are insignificantly different we assumed the two data sets where normal distributed based on the n>30 rule, and performed a two tailed T-Test.
-The T-Test produced a p-value of 0.17 which is bigger than a desired error margin ($\alpha$) of 5\%.
-The T-Test is therefore proving that no differences in RT exists within our data.
+To validate that the groups RTs are insignificantly different we assumed the two data sets where normal distributed based on the n>30 rule, and performed a two tailed t-test.
+The test produced a p-value of 0.17 which is bigger than a desired error margin ($\alpha$) of 5\%.
+The t-test is therefore proving that no differences in RT exists within our data.
 Regardless what the t-test says our standard deviations are indicating that something might be wrong with our data (see section \ref{sec:discussion}).
@@
 		\textbf{} & \textbf{Errors} & \textbf{Standard Deviation} & \textbf{Errors/User} \\ \hline
-		\textbf{HC} & 4 & 1.10 & 0.8 \\ \hline
-		\textbf{LC} & 19 & 3.49 & 3.8
+		\textbf{HCC} & 4 & 1.10 & 0.8 \\ \hline
+		\textbf{LCC} & 19 & 3.49 & 3.8
 	\end{tabular}
-	\caption{Number of user input errors registered in each group and a calculation of IEs per user in each group.
-The low color contrast interface produced 475\% more UIE compared to the high color contrast version.
+	\caption{Number of user input errors registered in each group and a calculation of input errors per user in each group.
+The low color contrast interface produced 475\% more input errors compared to the high color contrast version.
 A two tailed t-test also showed that there is a significant difference between the two versions.
-A high color contrast interface can therefore be a preferred design method if a low amount of user input errors is desired.
+A high color contrast interface can therefore be a preferred design method if a low amount of user input error is desired.
 	\label{tab:userIE}}
@@
 However we could see that the high color contrast interface was more reliable in performance when it comes to the amount of user input errors, according to our results.
+
 What we have seen in our collected test data can strongly negotiate the legibility of the results.
@@
 We found that we had randomly received negative RTs which in theory should be completely impossible.
-We were prepared that the timestamps could be off sync due to individual system clocks and no boot pairing.
-This would have resulted in a consistent off sync.
+We were prepared that the timestamps could be off sync due to individual system clocks and no boot up pairing.
+However this would only have resulted in a consistent off sync.
 Instead we got inconsistent hick ups in our timestamps.
@@
 Our conclusion is that HCC interfaces are the preferred method to design interfaces as they deliver a more stable user interaction pattern.
-Apart from this, smart phone web based applications should only be used if sometimes slow technology, user input errors and long reaction times from the user can be accepted.
+Apart from this, smart phone web based applications should only be used if sometimes slow technology, user input errors and long reaction times from the users can be accepted.
 
@@
 The main drawback of this study is the corrupt data set.
-Something to have in mind when we draw any conclusions out of the results.
-This problem could be solved by simply rerunning the whole test using a native smart phone application instead of a web based solution.
+This has to be in mind when we draw any conclusions out of the results.
+The problem could most probably be solved by simply rerunning the complete test using a native smart phone application instead of a web based solution.
 
@@
 It is possible to think that the patterns that slightly appeared in our results will appear even more significant with a larger group of test subjects.
-	\item Our collected test data can be downloaded and used freely to investigate other aspects not mentioned in this paper.
+	\item Our collected test data can be downloaded\footnote{Download here~\url{https://goo.gl/x8URSB}} and used freely to investigate other aspects not mentioned in this paper.
 One proposal is to look at the different shapes and try to detect possible error patterns between them.

### 2015-11-25 Paper.tex
Final

@@
 This study aims to investigate if it is possible to receive better user performance when using a high color contrast compared to a low color contrast touch screen interface in a mobile web application.
-The performance was measured by combining the time each user took to respond to instructions (reaction time) and the number of input errors from the user.
-Our result shows that the low color contrast interface produced 475\% more user input errors compared to the high color contrast interface.
+The performance was measured by combining the time each user took to respond to instructions (reaction time) and the number of input errors the user made.
+Received test data appeared to be corrupt, most probably due to limitations in web application technology, despite this our result show that the low color contrast interface produced 475\% more user input errors compared to the high color contrast interface.
 No difference in reaction time could be found between the two versions.
@@
 
-Earlier studies completed in this field has explored how we perceive different color contrast and how it can affect our reading performance~\cite{wu2003improving}.
+Earlier studies completed in this field have explored how we perceive different color contrast and how it can affect our reading performance~\cite{wu2003improving}.
 It has also been proved that chromaticity, contrast, and cone opponency in color space can affect RTs~\cite{mckeefry2003simple}.
-Many best practices for Mobile development have also shown that "requirements for sufficient color contrast"~\cite{marcus2013design} must be met to best exaggerate the content.
+Many best practices for mobile development have also shown that "requirements for sufficient color contrast"~\cite{marcus2013design} must be met to best exaggerate the content.
 Still the question remains, can a high color contrast interface increase the the reaction time and decrease the amount of user input errors?
@@
 	\includegraphics[width=\textwidth]{application}
-	\caption{Our two versions of the application designed with different color contrast.
-To the left the low color contrast interface and to the right the high color contrast interface.
+	\caption{Our two versions of the application designed with different contrast.
+To the left the low contrast interface and to the right the high contrast interface.
 The application and its interface was designed specifically for this test.
+The bottom menu was added to give the interface more of a complete application feel.
 	\label{fig:application}}
@@
 
-We designed the application by following design guidelines given here~\cite{hoober2011designing}~\cite{johnson2013designing}~\cite{gong2004guidelines}~\cite{norman2013design}.
+We designed the application by following design guidelines given here~\cite{hoober2011designing,johnson2013designing,gong2004guidelines,norman2013design}.
 These guidelines can be seen as a set of rules to follow when designing any kind of user interface.
@@
 Instructions were given in a series of 20.
-Between each instruction there was a delay set to be between 2.5 - 4 seconds.
+Between each instruction there was a delay set to be between 2.5 and 4 seconds.
 Each time a new symbol where showed a timestamp were logged in a unique user instruction file.
@@
 
-We tested each version of the application on 5 persons, all within the same age group (20-30) and with a variety of backgrounds.
+We tested each version of the application on five persons, all within the same age group (20-30) and with a variety of backgrounds.
 In total we got 10 test results with a gender split of 50\% women and 50\% men that grouped into LCC and HCC.
@@
 Our data received from the tests consisted of UNIX timestamps\footnote{More info at: \url{http://www.unixtimestamp.com/}} measured in milliseconds.
-Each time the user interacted with the application it registered which button that was pressed and saved it together with a UNIX timestamp.
-Equally, every time the instruction program showed a new symbol it logged the symbol together with a UNIX timestamp.
+Each time the user interacted with the application it registered which button that was pressed and saved it together with a timestamp.
+Equally, every time the instruction program showed a new symbol it logged the symbol together with a timestamp.
 As a result we received two data sets of symbols with corresponding timestamps for each test person, resulting in a total of 200 records.
@@
 From our results we can not draw any statistically significant differences in reaction time between the two groups high color contrast and low color contrast.
-This is most probably due to corrupt test data, a result from limitations in web application technology, see section \ref{sec:discussion}.
+This is most probably due to corrupt test data, a result from limitations in web application technology, see Section \ref{sec:discussion}.
 With user input errors we found that the low color contrast group produced significantly more user input errors than the hight color contrast group.
@@
 \subsection{Input Errors (IE)}
-None of the groups where completely free from user input errors. As can be seen in table~\ref{tab:userIE}, users that were given the LCC interface produced 475\% more UIE than the HCC group.
+None of the groups where completely free from user input errors. As can be seen in Table~\ref{tab:userIE}, users that were given the LCC interface produced 475\% more UIE than the HCC group.
 
@@
 It remains to answer if our results applies on all other systems.
-This is also a way of isolating some of the affecting parameters mentioned in~\ref{subsec:drawbacks}.
+This is also a way of isolating some of the affecting parameters mentioned in Section~\ref{subsec:drawbacks}.
 \end{itemize}

### 2016-01-03 Paper_revised.tex
revision

--- 2015-11-25 Paper.tex
@@
 
-\title{Can a High Color Contrast Touch Interface Increase User Reaction Time when Using a Smart Phone Web Based Application.}
+\title{Can a High Color Contrast Touch Interface Increase User Reaction Time when Using a Smart Phone Web Based Application?}
 
@@
 \begin{abstract}
-This study aims to investigate if it is possible to receive better user performance when using a high color contrast compared to a low color contrast touch screen interface in a mobile web application.
+This study aims to investigate if it is possible to receive better user performance when using a high-color-contrast compared to a low-color-contrast touch screen interface in a mobile web application.
 The performance was measured by combining the time each user took to respond to instructions (reaction time) and the number of input errors the user made.
@@
 The main goal with this paper is to evaluate if color contrast has a significant impact on usability in web based smart-phone applications.
-Consumer touch screen devices such as smart-phones have rapidly increased in amount and availability recent years.
-The touch screen technology have made great advances~\cite{jennings2013touch} and it is frequently used as a way of receiving user input.
+Consumer touch screen devices such as smart-phones have rapidly increased in number and availability recent years.
+The touch screen technology has made great advances~\cite{jennings2013touch} and it is frequently used as a way of receiving user input.
 When this technology moves to a broader audience, higher demands on usability needs to be set~\cite{gong2004guidelines}.
 To further explore how usability can be improved using touch screen technology we have in this paper investigated if reaction time (the time it takes for a user to react on instructions, further referred to as RT in this paper) and user input errors (the number of user input errors when interacting with a system, further referred to as UIE in this paper) can reach better results by increasing color contrast within the interface.
-Better results are assumed as faster RTs and less number of UIEs.
+With "better results" we mean fewer UIEs and faster RTs.
+Increased number of user input errors means that users repeatedly presses the wrong buttons which tells us that it is hard to accomplish desired tasks.
+Faster reaction times does not necessarily mean "better", but in this experiment we had tasks that should be performed as fast as possible which led us to the conclusion, faster reaction times are "better".
+
+Contrast is determined by the difference in color and brightness of an object and objects within the same field of view.
+High contrast is the degree of difference between dark and light approaches the maximum possible difference.
+Low contrast is the opposite.
 
@@
 It has also been proved that chromaticity, contrast, and cone opponency in color space can affect RTs~\cite{mckeefry2003simple}.
-Many best practices for mobile development have also shown that "requirements for sufficient color contrast"~\cite{marcus2013design} must be met to best exaggerate the content.
+Many best practices for mobile development have also shown that "requirements for sufficient color contrast"~\cite{marcus2013design} must be met to best amplify the content.
 Still the question remains, can a high color contrast interface increase the the reaction time and decrease the amount of user input errors?
@@
 High RTs and low UIEs are especially desirable when designing user interfaces for situations with high demands on quick user input and low error tolerance such as in emergency situations.
-The results of this paper can be used by any designer or developer.
+The results of studies like this are especially useful for designers and front end developers.
 
@@
 The application exists in two versions, one with low color contrast (referred to as LCC in this paper) and one with high color contrast (referred to as HCC in this paper) interface as can be seen in Fig~\ref{fig:application}.
-We conducted an A/B test to measure the performance between the versions.
+We conducted an A/B test to measure the performance difference between the versions.
 
@@
 
-We designed the application by following design guidelines given here~\cite{hoober2011designing,johnson2013designing,gong2004guidelines,norman2013design}.
+We designed the application by following design guidelines introduced and presented here~\cite{hoober2011designing,johnson2013designing,gong2004guidelines,norman2013design}.
 These guidelines can be seen as a set of rules to follow when designing any kind of user interface.
@@
 
-The application consists of 4 buttons\footnote{On screen button}, each button representing a function.
+The application consists of 4 buttons\footnote{On-screen button}, each button representing a function.
 To differentiate each button from the others we put a unique shape in each button.
@@
 The test persons were told to press the representative shape in the application as fast as they could in order to measure the reaction time.
-If they pressed the wrong button they were told to continue the test by pressing the right button, the application registered this as an UIE.
+If they realized that they pressed the wrong button they were just told to continue the test by pressing the right button as fast as they realized.
+the application registered all wrong, non-matching input as an UIE.
 Each test was performed indoors with varying surroundings such as different lightning conditions and noise levels.
@@
 The calculation of RT did not take in consideration if user input was a match with the instruction or not.
-It was still considered as an reaction.
+It was still considered as a reaction.
 
@@
 \section{Result}
-From our results we can not draw any statistically significant differences in reaction time between the two groups high color contrast and low color contrast.
+From our results we can not draw any statistically significant conclusions about differences in reaction time between the two groups high color contrast and low color contrast.
 This is most probably due to corrupt test data, a result from limitations in web application technology, see Section \ref{sec:discussion}.
@@
 \subsection{Reaction Times (RT)}
-Table~\ref{tab:groupRT} shows our average reaction time and standard deviation for each group.
+Table~\ref{tab:groupRT} shows the average reaction time and standard deviation for each group.
 According to the results people in the high color contrast group had insignificant slower reaction times compared to the ones in the low color contrast group.
@@
 
-To validate that the groups RTs are insignificantly different we assumed the two data sets where normal distributed based on the n>30 rule, and performed a two tailed t-test.
+To check if the RTs in the two groups are significantly different we assumed the two data sets where normal distributed based on the n>30 preference, and performed a two tailed t-test.
 The test produced a p-value of 0.17 which is bigger than a desired error margin ($\alpha$) of 5\%.
-The t-test is therefore proving that no differences in RT exists within our data.
+This shows that the difference in RT between the two groups is not statistically significant.
 Regardless what the t-test says our standard deviations are indicating that something might be wrong with our data (see section \ref{sec:discussion}).
 
-\subsection{Input Errors (IE)}
+\subsection{Input Errors (IE)}\label{subsec:InputErrors}
 None of the groups where completely free from user input errors. As can be seen in Table~\ref{tab:userIE}, users that were given the LCC interface produced 475\% more UIE than the HCC group.
@@
 \section{Discussion}\label{sec:discussion}
-Our test results have shown that we can not increase the user reaction time by using a high color contrast interface when using a smart phone web based application.
+From our test results we cannot draw any conclusions about differences in reaction time between the high color contrast interface and the low color contrast interface.
 However we could see that the high color contrast interface was more reliable in performance when it comes to the amount of user input errors, according to our results.
@@
 However this would only have resulted in a consistent off sync.
-Instead we got inconsistent hick ups in our timestamps.
+Instead we got inconsistent hiccups in our timestamps.
 We suspect this is a result from either hardware limitations or limitations in the JavaScript\footnote{A prototype based dynamic scripting language} engine for web applications on Android.
 
-Our conclusion is that HCC interfaces are the preferred method to design interfaces as they deliver a more stable user interaction pattern.
-Apart from this, smart phone web based applications should only be used if sometimes slow technology, user input errors and long reaction times from the users can be accepted.
+Although we can not draw any conclusions out from the results we have learned that smart phone web based applications should only be used if sometimes slow technology, user input errors and long reaction times from the user can be accepted.
+The HCC interface could also be seen as a preferred design method, even if the data was corrupt, because the users performed more consistent with UIEs compared to the users in the LCC group, see number of UIEs and their standard deviations in~\ref{subsec:InputErrors}.
 
@@
 \begin{description}
-	\item[Small test group.] To be able to get a more statistical valid result the test group has to be bigger.
+	\item[Small test group.] To be able to get a more statistical valid result the test group has to be bigger. A good rule of thumb is at least 30.
 	\item[Many affecting parameters.] The prototype is simple in its appearance but there are still many parameters that can affect the users interaction and their RTs.
@@
 All this, and more, should have been researched and taken into account if done again.
-	\item[Limited test environment.] Our tests were made using an Android based smart-phone\footnote{OnePlus Two \url{https://oneplus.net/2}} and the application were made using HTML5\footnote{HyperText Markup Language, markup standard for WWW}, CSS3\footnote{Cascading Style Sheet, styling standard for WWW} and JavaScript.
-We can not surely imply, without testing, that the same results would appear on an iPhone or any other smart-phone or even with a native application.
+	\item[Limited test environment.] Our tests were made using an Android based smart-phone\footnote{OnePlus Two \url{https://oneplus.net/2}} and the application was made using HTML5\footnote{HyperText Markup Language, markup standard for WWW}, CSS3\footnote{Cascading Style Sheet, styling standard for WWW} and JavaScript.
+We can not surely imply, without testing, that we would get the same results on an iPhone or any other smart-phone, or even with a native application.
 \end{description}

### 2016-01-04 Paper_revised.tex
updated revision
revised to proceeding

@@
 \usepackage[T1]{fontenc}  %% needed for special characters (umlaut)
-\usepackage[utf8]{inputenc}
+\usepackage[latin1]{inputenc}
 \usepackage{graphicx}     %% for graphical things such as including pictures
@@
 % Albins Packages
-\usepackage{array}
+% \usepackage{array}
 
@@
 The performance was measured by combining the time each user took to respond to instructions (reaction time) and the number of input errors the user made.
-Received test data appeared to be corrupt, most probably due to limitations in web application technology, despite this our result show that the low color contrast interface produced 475\% more user input errors compared to the high color contrast interface.
+Received test data appeared to be corrupt, most probably due to limitations in web application technology, despite this our result shows that the low color contrast interface produced 475\% more user input errors compared to the high color contrast interface.
 No difference in reaction time could be found between the two versions.
@@
 To further explore how usability can be improved using touch screen technology we have in this paper investigated if reaction time (the time it takes for a user to react on instructions, further referred to as RT in this paper) and user input errors (the number of user input errors when interacting with a system, further referred to as UIE in this paper) can reach better results by increasing color contrast within the interface.
-With "better results" we mean fewer UIEs and faster RTs.
+With "better results" we intend to mean fewer UIEs and faster RTs.
 Increased number of user input errors means that users repeatedly presses the wrong buttons which tells us that it is hard to accomplish desired tasks.
@@
 Contrast is determined by the difference in color and brightness of an object and objects within the same field of view.
-High contrast is the degree of difference between dark and light approaches the maximum possible difference.
-Low contrast is the opposite.
+High contrast is the degree of difference between dark and light where it approaches the maximum possible difference.
+Low contrast is the opposite, low degree of difference between dark light.
 
